---
title: "COVID19 UK"
author: "Heinrich Peters"
date: "4/23/2020"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# MAC
 knitr::opts_knit$set(root.dir = '/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Data/UK')
 
library(lmerTest)
library(nlme)
library(psych)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(party)
library(doParallel)
library(changepoint)
library(survival)
library(survminer)
 
source('/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Code/COVID19_functions.R')
```

# Prepare data

### Read and format prevalence data
```{r warning=FALSE, message=FALSE}
df_uk_prev <- read_csv('UK_timeseries_prep_2005.csv')

df_uk_prev <- df_uk_prev %>% 
  select(ut_area, date, rate) %>% 
  rename(rate_day = rate) %>%
  mutate(date = as.Date(date, "%d%b%Y"))

df_uk_prev2 <- read_csv('UK_timeseries_prep_0506_laua_all.csv')

df_uk_prev2 <- df_uk_prev2 %>% 
  select(laua, date, males, popdens, manufacturing, tourism, health,
         academic, medage, conservative, airport_dist, medinc, open,
         extra, agree, neuro, sci, rate) %>%
  rename(pers_o = open, 
         pers_c = sci,
         pers_e = extra,
         pers_a = agree,
         pers_n = neuro,
         rate_day = rate,
         age = medage,
         male = males,
         manufact = manufacturing,
         healthcare = health,
         academics = academic) %>%
  mutate(date = as.Date(date, "%d%b%Y"))

df_uk_prev2 %>% select(-date, -rate_day) %>% 
  distinct() %>% write_csv('df_uk_pers_laua.csv')

df_uk_prev2 %>% select(laua, date, rate_day) %>% write_csv('uk_prev_laua.csv')
```

### Personality
```{r warning=FALSE, message=FALSE}
df_uk_pers <- read_csv('timeseries_uk_utla_march9_april_09.csv')

df_uk_pers <- df_uk_pers %>% 
  select(ut_area, open, agree, neuro, sci, extra) %>% 
  dplyr::rename(pers_o = open, 
         pers_c = sci,
         pers_e = extra,
         pers_a = agree,
         pers_n = neuro) %>%
  distinct()

df_uk_pers %>% write_csv('df_uk_pers_ut.csv')

df_uk_pers_nuts <- read_csv('UK_socdist_fb_nuts3.csv')

df_uk_pers_nuts <- df_uk_pers_nuts %>% 
  select(nuts3, open, sci, extra, agree, neuro) %>%
  dplyr::rename(pers_o = open, 
                pers_c = sci,
                pers_e = extra,
                pers_a = agree,
                pers_n = neuro) %>%
  distinct()
```

### Social distancing
```{r, warning=FALSE}

fb_files <- list.files('../FB Data/UK individual files',
                       '*.csv', full.names = T)

df_uk_socdist <- fb_files %>% 
  map(read.csv) %>% bind_rows()

df_uk_socdist <- df_uk_socdist %>%
  select(ds, all_day_bing_tiles_visited_relative_change,
         all_day_ratio_single_tile_users, external_polygon_id) %>%
  rename(date = ds,
         nuts3 = external_polygon_id,
         socdist_tiles = all_day_bing_tiles_visited_relative_change,
         socdist_single_tile = all_day_ratio_single_tile_users) %>%
  mutate(nuts3 = as.character(nuts3),
         date = as.Date(date)) %>%
  arrange(nuts3, date) %>%
  drop_na()

```


```{r}
df_uk_socdist %>% select(nuts3) %>% distinct() %>% nrow()
```

### Controls 
```{r warning=FALSE, message=FALSE}
df_uk_ctrl_nuts <- read_csv("controls_UK_nuts3.csv")
df_uk_ctrl_nuts <- df_uk_ctrl_nuts %>% select(-nuts3_name)
df_uk_ctrl_nuts <- df_uk_ctrl_nuts %>% rename(
         age = medage,
         male = males,
         manufact = manufacturing,
         healthcare = health,
         academics = academic)


df_uk_ctrl_ut <- read_csv("controls_UK_ut.csv")
df_uk_ctrl_ut <- df_uk_ctrl_ut %>% select(-ut_name)
df_uk_ctrl_ut <- df_uk_ctrl_ut %>% rename(
         age = medage,
         male = males,
         manufact = manufacturing,
         healthcare = health,
         academics = academic)


```

### Merge prevalence data 
```{r}
df_uk_prev <- df_uk_prev %>% 
  plyr::join(df_uk_pers, by='ut_area') %>% 
  plyr::join(df_uk_ctrl_ut, by='ut_area')

# create sequence of dates
date_sequence <- seq.Date(min(df_uk_prev$date),
                          max(df_uk_prev$date), 1)
                     
# create data frame with time sequence
df_dates = tibble(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# merge day index with gps data
df_uk_prev = df_uk_prev %>% 
  merge(df_dates, by='date') %>% 
  arrange(ut_area) %>%
  as_tibble()

df_uk_prev %>% select(-date, -rate_day, -time) %>% 
  distinct() %>% write_csv('df_uk_pers_ut.csv')
```

```{r}
# create sequence of dates
date_sequence <- seq.Date(min(df_uk_prev2$date),
                          max(df_uk_prev2$date), 1)
                     
# create data frame with time sequence
df_dates = tibble(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# merge day index with gps data
df_uk_prev2 = df_uk_prev2 %>% 
  merge(df_dates, by='date') %>% 
  arrange(laua) %>%
  as_tibble()
```

### Merge social distancing data
```{r}
df_uk_socdist <- df_uk_socdist %>% 
  plyr::join(df_uk_ctrl_nuts, by='nuts3') %>%
  plyr::join(df_uk_pers_nuts, by='nuts3')

# create sequence of dates
date_sequence <- seq.Date(min(df_uk_socdist$date),
                          as.Date('2020-04-28'), 1)
                     
# create data frame with time sequence
df_dates = tibble(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# merge day index with gps data
df_uk_socdist = df_uk_socdist %>% 
  inner_join(df_dates, by='date') %>% 
  arrange(nuts3) %>%
  as_tibble()

df_uk_socdist %>% select(-date, -socdist_tiles, -socdist_single_tile, -time) %>% 
  distinct() %>% write_csv('df_uk_pers_nuts.csv')

```

### Check timeframes 
```{r}
df_uk_prev$date %>% summary()
df_uk_socdist$date %>% summary()
```

### Control for weekend effect in social distancing
```{r}
easter <- seq.Date(as.Date('2020-04-10'), as.Date('2020-04-13'), 1)

df_uk_loess <- df_uk_socdist %>% 
  mutate(weekday = format(date, '%u')) %>% 
  filter(!(weekday %in% c('6','7') | date %in% easter)) %>% 
  split(.$nuts3) %>%
  map(~ loess(socdist_single_tile ~ time, data = .)) %>%
  map(predict, 1:max(df_uk_socdist$time)) %>% 
  bind_rows() %>% 
  gather(key = 'nuts3', value = 'loess') %>% 
  group_by(nuts3) %>% 
  mutate(time = row_number())

df_uk_loess_2 <- df_uk_socdist %>% 
  mutate(weekday = format(date, '%u')) %>% 
  filter(!(weekday %in% c('6','7') | date %in% easter)) %>% 
  split(.$nuts3) %>%
  map(~ loess(socdist_tiles ~ time, data = .)) %>%
  map(predict, 1:max(df_uk_socdist$time)) %>% 
  bind_rows() %>% 
  gather(key = 'nuts3', value = 'loess') %>%
  rename(loess_2 = loess) %>%
  group_by(nuts3) %>% 
  mutate(time = row_number())

df_uk_socdist <- df_uk_socdist %>% 
  merge(df_uk_loess, by=c('nuts3', 'time')) %>% 
  merge(df_uk_loess_2, by=c('nuts3', 'time')) %>% 
  mutate(weekday = format(date, '%u')) %>% 
  mutate(socdist_single_tile_clean = ifelse(weekday %in% c('6','7') | date %in% easter, 
                                            loess, socdist_single_tile),
         socdist_tiles_clean = ifelse(weekday %in% c('6','7') | date %in% easter, 
                                            loess_2, socdist_tiles)) %>%
  arrange(nuts3, time) %>% 
  select(-weekday)

df_uk_socdist <- df_uk_socdist %>% drop_na() %>% mutate(time = time-1)
```

### Pick cleaned social distancing metrics
```{r}

df_uk_socdist <- df_uk_socdist %>% 
  mutate(socdist_single_tile = socdist_single_tile_clean,
         socdist_tiles = socdist_tiles_clean) %>% 
  select(-loess, -loess_2, -socdist_single_tile_clean, -socdist_tiles_clean)

```

### Rescale Data
```{r}
lvl2_scaled_ut <- df_uk_prev %>% 
  dplyr::select(-time, -date, -rate_day) %>% 
  distinct() %>% 
  mutate_at(vars(-ut_area), scale)

lvl1_scaled_ut <- df_uk_prev %>% select(ut_area, date, time, rate_day)

df_uk_prev_scaled <- plyr::join(lvl1_scaled_ut, lvl2_scaled_ut, by = 'ut_area')
```

```{r}
lvl2_scaled_laua <- df_uk_prev2 %>% 
  dplyr::select(-time, -date, -rate_day) %>% 
  distinct() %>% 
  mutate_at(vars(-laua), scale)

lvl1_scaled_laua <- df_uk_prev2 %>% select(laua, date, time, rate_day)

df_uk_prev2_scaled <- plyr::join(lvl1_scaled_laua, lvl2_scaled_laua, by = 'laua')
```

```{r}
lvl2_scaled_nuts <- df_uk_socdist %>% 
  dplyr::select(-time, -date, -socdist_tiles, -socdist_single_tile) %>% 
  distinct() %>% 
  mutate_at(vars(-nuts3), scale)

lvl1_scaled_nuts <- df_uk_socdist %>% 
  select(nuts3, date, time, socdist_single_tile, socdist_tiles) %>% 
  mutate_at(vars(-nuts3, -time), scale)

df_uk_socdist_scaled <- plyr::join(lvl1_scaled_nuts, lvl2_scaled_nuts, by = 'nuts3')
```

# Define outcomes of interest
### COVID - Extract onset UT level
```{r}
# get onset day
df_uk_onset_prev <- df_uk_prev_scaled %>% 
  group_by(ut_area) %>% 
  mutate(rate = rate_day-lag(rate_day)) %>% 
  drop_na() %>%
  mutate(rate_cs = cumsum(rate)) %>% 
  filter(rate_cs > 0.1) %>%
  summarize(onset_prev = min(time))

# merge with county data
df_uk_onset_prev <- df_uk_prev_scaled %>% 
  select(-time, -date, -rate_day) %>%
  distinct() %>% 
  left_join(df_uk_onset_prev, by = 'ut_area')

# handle censored data
df_uk_onset_prev <- df_uk_onset_prev %>% 
  mutate(event = ifelse(is.na(onset_prev), 0, 1)) %>% 
  mutate(onset_prev = replace_na(onset_prev, as.numeric(diff(range(df_uk_prev$date)))+1))

df_uk_onset_prev$onset_prev %>% hist()
df_uk_onset_prev$onset_prev %>% mean()
```

### Extract slopes
```{r}
# cut time series before onset
df_uk_prev_scaled <- df_uk_prev_scaled %>% 
  group_by(ut_area) %>% 
  mutate(rate = rate_day-lag(rate_day)) %>% 
  drop_na() %>%
  mutate(rate_cs = cumsum(rate)) %>% 
  filter(rate_cs > 0.1) %>%
  mutate(time = time-min(time)+1) %>%
  ungroup() %>%
  filter(time <= 30) %>%
  select(-rate_cs)

# extract slope prevalence
df_uk_slope_prev <- df_uk_prev_scaled %>% split(.$ut_area) %>% 
  map(~ lm(log(rate_day+1) ~ time, data = .)) %>%
  map(coef) %>% 
  map_dbl('time') %>% 
  as.data.frame() %>% 
  rownames_to_column('ut_area') %>% 
  rename(slope_prev = '.')

# merge with county data
df_uk_slope_prev <- df_uk_onset_prev %>% 
  inner_join(df_uk_slope_prev, by = 'ut_area') %>%
  drop_na()

# standardize slopes
df_uk_slope_prev <- df_uk_slope_prev %>% 
  mutate(slope_prev = scale(slope_prev),
         onset_prev = scale(onset_prev))
```

### Explore distributions
```{r}
df_uk_onset_prev %>% ggplot(aes(onset_prev)) + geom_histogram()
df_uk_slope_prev %>% ggplot(aes(slope_prev)) + geom_histogram()
```


### Extract COVID onset - LAD level
```{r}

# get onset day
df_uk_onset_prev_laua <- df_uk_prev2_scaled %>% 
  group_by(laua) %>% 
  mutate(rate = rate_day-lag(rate_day)) %>% 
  drop_na() %>%
  mutate(rate_cs = cumsum(rate)) %>% 
  filter(rate_cs > 0.1) %>%
  summarize(onset_prev = min(time))
  
# merge with county data
df_uk_onset_prev_laua <- df_uk_prev2_scaled %>% 
  select(-time, -date, -rate_day) %>%
  distinct() %>% 
  left_join(df_uk_onset_prev_laua, by = 'laua')

# handle censored data
df_uk_onset_prev_laua <- df_uk_onset_prev_laua %>% 
  mutate(event = ifelse(is.na(onset_prev), 0, 1)) %>% 
  mutate(onset_prev = replace_na(onset_prev, as.numeric(diff(range(df_uk_prev2$date)))+1))

```

### Extract slopes
```{r}

# cut time series before onset
df_uk_prev2_scaled <- df_uk_prev2_scaled %>% 
  group_by(laua) %>% 
  mutate(rate = rate_day-lag(rate_day)) %>% 
  drop_na() %>%
  mutate(rate_cs = cumsum(rate)) %>% 
  filter(rate_cs > 0.1) %>%
  mutate(time = time-min(time)+1) %>%
  ungroup() %>%
  filter(time <= 30) %>%
  select(-rate_cs)

# extract slope prevalence
df_uk_slope_prev_laua <- df_uk_prev2_scaled %>% split(.$laua) %>% 
  map(~ lm(log(rate_day+1) ~ time, data = .)) %>%
  map(coef) %>% 
  map_dbl('time') %>% 
  as.data.frame() %>% 
  rownames_to_column('laua') %>% 
  rename(slope_prev = '.')

# merge with county data
df_uk_slope_prev_laua <- df_uk_onset_prev_laua %>% 
  left_join(df_uk_slope_prev_laua, by = 'laua') %>%
  mutate(slope_prev = replace_na(slope_prev, 0))

# standardize slopes
df_uk_slope_prev_laua <- df_uk_slope_prev_laua %>% 
  mutate(slope_prev = scale(slope_prev),
         onset_prev = scale(onset_prev))
```

### Explore distributions
```{r}
df_uk_onset_prev_laua %>% ggplot(aes(onset_prev)) + geom_histogram()
df_uk_slope_prev_laua %>% ggplot(aes(slope_prev)) + geom_histogram()
```

### Social Distancing - Change point analysis
```{r}
# keep only counties with full data
nuts_complete <- df_uk_socdist_scaled %>% 
  group_by(nuts3) %>% 
  summarize(n = n()) %>% 
  filter(n==max(.$n)) %>% 
  .$nuts3

# run changepoint analysis
df_uk_socdist_cpt_results <- df_uk_socdist_scaled %>% 
  select(nuts3, socdist_single_tile) %>%
  filter(nuts3 %in% nuts_complete) %>% 
  split(.$nuts3) %>%
  map(~ cpt.meanvar(as.vector(.$socdist_single_tile),
                    #penalty = 'Asymptotic',
                    class=TRUE,
                    param.estimates=TRUE,
                    Q=1,
                    test.stat = 'Normal'))

df_uk_socdist_cpt_results_2 <- df_uk_socdist_scaled %>% 
  select(nuts3, socdist_tiles) %>%
  filter(nuts3 %in% nuts_complete) %>% 
  split(.$nuts3) %>%
  map(~ cpt.meanvar(as.vector(.$socdist_tiles),
                    #penalty = 'Asymptotic',
                    class=TRUE,
                    param.estimates=TRUE,
                    Q=1,
                    test.stat = 'Normal'))

# calculate change point
df_uk_socdist_cpt_day <- df_uk_socdist_cpt_results %>% 
  map(cpts) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cpt_day_socdist = '.') %>%
  rownames_to_column('nuts3')

df_uk_socdist_cpt_day_2 <- df_uk_socdist_cpt_results_2 %>% 
  map(cpts) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cpt_day_socdist_2 = '.') %>%
  rownames_to_column('nuts3')

# calculate mean differences
df_uk_socdist_cpt_mean_diff <- df_uk_socdist_cpt_results %>% 
  map(param.est) %>% 
  map(~ .$mean) %>% 
  map(~ .[2]) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mean_diff_socdist = '.') %>%
  rownames_to_column('nuts3')

df_uk_socdist_cpt_mean_diff_2 <- df_uk_socdist_cpt_results_2 %>% 
  map(param.est) %>% 
  map(~ .$mean) %>% 
  map(~ -.[2]) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mean_diff_socdist_2 = '.') %>%
  rownames_to_column('nuts3')

# calculate means 
df_uk_socdist_mean <- df_uk_socdist_scaled %>% 
  group_by(nuts3) %>%
  summarize(mean_socdist = mean(socdist_single_tile))

df_uk_socdist_mean_2 <- df_uk_socdist_scaled %>% 
  group_by(nuts3) %>%
  summarize(mean_socdist_2 = -mean(socdist_tiles))

# merge with county data
nuts_ut_key <- read_csv('nuts3_ut.csv')

df_uk_cpt_socdist <- df_uk_socdist_scaled %>% 
  select(-time, -date, -socdist_single_tile, -socdist_tiles) %>%
  distinct() %>% 
  left_join(df_uk_socdist_cpt_day, by='nuts3') %>%
  left_join(df_uk_socdist_cpt_day_2, by='nuts3') %>%
  left_join(df_uk_socdist_cpt_mean_diff, by='nuts3') %>%
  left_join(df_uk_socdist_cpt_mean_diff_2, by='nuts3') %>%
  left_join(df_uk_socdist_mean, by='nuts3') %>%
  left_join(df_uk_socdist_mean_2, by='nuts3') %>%
  left_join(nuts_ut_key, by='nuts3') %>% 
  left_join(select(df_uk_onset_prev, ut_area, onset_prev), by='ut_area') %>%
  left_join(select(df_uk_slope_prev, ut_area, slope_prev), by='ut_area') %>%
  select(-ut_area)

# standardize mean/var differences
df_uk_cpt_socdist <- df_uk_cpt_socdist %>% 
  mutate(mean_diff_socdist = scale(mean_diff_socdist),
         mean_diff_socdist_2 = scale(mean_diff_socdist_2),
         mean_socdist = scale(mean_socdist),
         mean_socdist_2 = scale(mean_socdist_2))

# handle censored data
df_uk_cpt_socdist <- df_uk_cpt_socdist %>% 
  mutate(cpt_day_socdist = ifelse(is.na(cpt_day_socdist), 
                                  as.numeric(diff(range(df_uk_cpt_socdist$date))), 
                                  cpt_day_socdist)) %>% 
  mutate(event = ifelse(cpt_day_socdist >= 
                          as.numeric(diff(range(df_uk_socdist$date))), 0, 1))

```

```{r}
df_uk_cpt_socdist$cpt_day_socdist %>% hist()
df_uk_cpt_socdist$mean_diff_socdist %>% hist()
df_uk_cpt_socdist$mean_socdist %>% hist()


df_uk_cpt_socdist$cpt_day_socdist_2 %>% hist()
df_uk_cpt_socdist$mean_diff_socdist_2 %>% hist()
df_uk_cpt_socdist$mean_socdist_2 %>% hist()

```

```{r}

for(i in head(df_uk_socdist_cpt_results, 5)){
  plot(i)
}

```
```{r}

for(i in head(df_uk_socdist_cpt_results_2, 5)){
  plot(i)
}

```

# Fit models
### Predict COVID onset
```{r}
uk_cox_prev_onset <- run_analyses(y = 'onset_prev',  data = df_uk_slope_prev_laua, model = 'cox')
```

### Predict COVID growth
```{r}
uk_lm_prev_slope <- run_analyses(y = 'slope_prev',  data = df_uk_slope_prev_laua, model = 'lm')
```

### Predict socdist change points
```{r}
uk_cox_socdist_cpt <- run_analyses(y = 'cpt_day_socdist_2',  data = df_uk_cpt_socdist, model = 'cox')
```

### Predict socdist means
```{r}
uk_lm_socdist_mean <- run_analyses(y = 'mean_socdist_2',  data = df_uk_cpt_socdist, model = 'lm')
```

# Export data 
```{r}

uk_list_results <- list(uk_cox_prev_onset, uk_lm_prev_slope,
                         uk_cox_socdist_cpt, uk_lm_socdist_mean)

uk_results_names <- list('uk_cox_prev_onset', 'uk_lm_prev_slope',
                      'uk_cox_socdist_cpt', 'uk_lm_socdist_mean')

names(uk_list_results) <- uk_results_names

save(uk_list_results, file="uk_list_results.RData")
```

# Extract results
### Results - predict COVID onset
```{r}
uk_agg_prev_onset <- uk_list_results$uk_cox_prev_onset %>% extract_all()
```

### Results - predict COVID growth
```{r}
uk_agg_prev_slope <- uk_list_results$uk_lm_prev_slope %>% extract_all()
```

### Results - predict socdist start
```{r}
uk_agg_socdist_cpt <- uk_list_results$uk_cox_socdist_cpt %>% extract_all()
```

### Results - predict socdist means
```{r}
uk_agg_socdist_mean <- uk_list_results$uk_lm_socdist_mean %>% extract_all()
```


### Save aggregated results
```{r}
uk_agg <- list(uk_agg_prev_onset,
               uk_agg_prev_slope,
               uk_agg_socdist_cpt,
               uk_agg_socdist_mean
               )

names(uk_agg) <- uk_results_names

save(uk_agg, file="uk_agg.RData")

uk_agg
```



```{r}

write_csv(df_uk_slope_prev, '/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Delivery/df_uk_slope_prev.csv')
write_csv(df_uk_cpt_socdist, '/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Delivery/df_uk_cpt_socdist.csv')

```