---
title: "COVID19 UK"
author: "Heinrich Peters"
date: "4/23/2020"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# MAC
 knitr::opts_knit$set(root.dir = '/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Data/UK')
 
library(lmerTest)
library(nlme)
library(psych)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(xtable)

```

# Prepare data

### Read and format data

### Prevalence 
```{r}

df_uk_covid <- read_csv('timeseries_uk_utla_march9_april_09.csv')
df_uk_covid$time %>% summary()

df_uk <- df_uk_covid %>% filter(time <=22) %>% 
  dplyr::rename(pers_o = open, 
         pers_c = sci,
         pers_e = extra,
         pers_a = agree,
         pers_n = neuro) %>%
  select(-ut_name, -areaname, -poptotal) %>%
  drop_na()

df_uk %>% head()

```

### Social distancing
```{r}

df_uk_socdist <- read_csv('UK_socdist_fb_nuts3.csv')
df_uk_socdist$date %>% summary()

df_uk_socdist <- df_uk_socdist %>% select(-runday) %>%
  filter(date >= '2020-03-09' & date <= '2020-03-31') %>%
  group_by(nuts3) %>% 
  mutate(time = row_number()) %>%
  ungroup() %>% 
  dplyr::rename(pers_o = open, 
                pers_c = sci,
                pers_e = extra,
                pers_a = agree,
                pers_n = neuro) %>% 
  select(-nuts3_name) %>% 
  dplyr::rename(socdist_tiles = all_day_bing_tiles_visited_relat,
                socdist_single_tile = all_day_ratio_single_tile_users) %>%
  drop_na()

nuts_ut_key <- read_csv('nuts3_ut.csv')

df_uk_socdist <- nuts_ut_key %>% 
  plyr::join(select(df_uk, ut_area, time, rate_day), by = 'ut_area') %>%
  plyr::join(df_uk_socdist, by = c('nuts3', 'time')) %>% 
  select(-ut_area)

df_uk_socdist %>% head()

```

### Controls 
```{r}
df_uk_ctrl_nuts <- read_csv("controls_UK_nuts3.csv")
df_uk_ctrl_nuts <- df_uk_ctrl_nuts %>% select(-nuts3_name)
df_uk_ctrl_nuts


df_uk_ctrl_ut <- read_csv("controls_UK_ut.csv")
df_uk_ctrl_ut <- df_uk_ctrl_ut %>% select(-ut_name)
df_uk_ctrl_ut


```

### Merge data 
```{r}

df_uk <- df_uk %>% plyr::join(df_uk_ctrl_ut, by='ut_area')

df_uk_socdist <- df_uk_socdist %>% plyr::join(df_uk_ctrl_nuts, by='nuts3')


```


### Identify London areas
```{r}

nuts_london_inner <- c('UKI31','UKI32','UKI33','UKI34','UKI41',
                      'UKI42','UKI43','UKI44','UKI45')

nuts_london_outer <- c('UKI51','UKI52','UKI53','UKI54','UKI61',
                      'UKI62','UKI63','UKI71','UKI72','UKI73',
                      'UKI74','UKI75')

ut_london_inner <- c('E09000007','E09000001','E09000033','E09000013',
                    'E09000020','E09000032','E09000025','E09000012',
                    'E09000030','E09000014','E09000019','E09000023',
                    'E09000028','E09000022')

ut_london_outer <- c('E09000011','E09000004','E09000016','E09000002',
                    'E09000031','E09000026','E09000010','E09000006',
                    'E09000008','E09000029','E09000021','E09000024',
                    'E09000003','E09000005','E09000009','E09000017',
                    'E09000015','E09000018','E09000027')
```

```{r}

df_uk = df_uk %>% 
  mutate(london = ifelse(ut_area %in% ut_london_inner, 'london_inner', 
                       ifelse(ut_area %in% ut_london_outer, 'london_outer',
                              'country'))) %>%
  mutate(london = as.factor(london))

df_uk_socdist = df_uk_socdist %>% 
  mutate(london = ifelse(nuts3 %in% nuts_london_inner, 'london_inner', 
                       ifelse(nuts3 %in% nuts_london_outer, 'london_outer',
                              'country'))) %>%
  mutate(london = as.factor(london))

```


# Explore data

### Plot prevalence over time
```{r}

df_uk %>% ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=ut_area, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall prevalence over time")

pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

gg <- df_uk %>% mutate(prev_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.2), quantile(.[[i]], 0.8), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(prev_tail != 'center') %>%
  ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=ut_area, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~prev_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```


### Plot social distancing over time
```{r}

df_uk_socdist %>% ggplot(aes(x=time, y=socdist_single_tile)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall social distancing over time")

pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

gg <- df_uk_socdist %>% mutate(socdist_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.2), quantile(.[[i]], 0.8), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(socdist_tail != 'center') %>%
  ggplot(aes(x=time, y=socdist_single_tile)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~socdist_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```

### Explore differences between london and the rest 
```{r}

df_uk %>% ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=ut_area, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  facet_wrap(~london) +
  ggtitle("Overall prevalence over time")



```


```{r}
df_uk_socdist %>% ggplot(aes(x=time, y=socdist_single_tile)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  facet_wrap(~london) +
  ggtitle("Overall social distancing over time")
```

### Control for weekend effect 
```{r}

weekend <- c(6, 7, 13, 14, 20, 21)

df_uk_loess <- df_uk_socdist %>% filter(!time %in% weekend) %>% 
  split(.$nuts3) %>%
  map(~ loess(socdist_single_tile ~ time, data = .)) %>%
  map(predict, 1:23) %>% 
  bind_rows() %>% 
  gather(key = 'nuts3', value = 'loess') %>% 
  group_by(nuts3) %>% 
  mutate(time = row_number())

df_uk_socdist <- df_uk_socdist %>% merge(df_uk_loess, by=c('nuts3', 'time')) %>% 
  mutate(socdist_single_tile_clean = ifelse(time %in% weekend, loess,
                                            socdist_single_tile)) %>%
  arrange(nuts3, time)


df_uk_socdist %>% ggplot(aes(x=time, y=loess, group=nuts3)) +
  geom_line()

df_uk_socdist


```

```{r}

df_uk_socdist %>% ggplot(aes(x=time, y=socdist_single_tile_clean)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall social distancing over time")

pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

gg <- df_uk_socdist %>% mutate(socdist_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.2), quantile(.[[i]], 0.8), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(socdist_tail != 'center') %>%
  ggplot(aes(x=time, y=socdist_single_tile_clean)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~socdist_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```

```{r}

df_uk_socdist <- df_uk_socdist %>% mutate(socdist_single_tile = socdist_single_tile_clean) %>% 
  select(-loess, -socdist_single_tile_clean)

```

### Correlations
```{r}

df_uk %>% group_by(ut_area) %>% 
  summarize_if(is.numeric, mean, na.rm=T) %>% 
  select(-ut_area, -time) %>% 
  cor(use = 'pairwise.complete') %>% round(3)

df_uk_socdist %>% group_by(nuts3) %>% 
  summarize_if(is.numeric, mean, na.rm=T) %>% 
  select(-nuts3, -time) %>% 
  cor(use = 'pairwise.complete') %>% round(3)

```

# Modelling 
## Prepare functions

```{r}

# function calculates all relevant models
run_models <- function(y, lvl1_x, lvl2_x, lvl2_id, data, ctrls=F){

  # subset data
  data = data %>% 
    dplyr::select(all_of(y), all_of(lvl1_x), all_of(lvl2_x), all_of(lvl2_id), 
                  popdens, rate_day, all_of(y))
  data = data %>% 
    dplyr::rename(y = all_of(y),
           lvl1_x = all_of(lvl1_x),
           lvl2_x = all_of(lvl2_x),
           lvl2_id = all_of(lvl2_id)
           )
  
  # configure optimization procedure
  ctrl_config <- lmeControl(opt = 'optim', maxIter = 100, msMaxIter = 100)

  # baseline
  baseline <- lme(fixed = y ~ 1, random = ~ 1 | lvl2_id, 
                    data = data,
                    correlation = corAR1(),
                  control = ctrl_config,
                  method = 'ML')

  # random intercept fixed slope
  random_intercept <- lme(fixed = y ~ lvl1_x + lvl2_x, 
                          random = ~ 1 | lvl2_id,
                            data = data,
                            correlation = corAR1(),
                  control = ctrl_config,
                  method = 'ML')

  # random intercept random slope
  random_slope <- lme(fixed = y ~ lvl1_x + lvl2_x, 
                      random = ~ lvl1_x | lvl2_id, 
                        data = data,
                        correlation = corAR1(),
                  control = ctrl_config,
                  method = 'ML')

  # cross level interaction
  interaction <- lme(fixed = y ~ lvl1_x * lvl2_x, 
                     random = ~ lvl1_x | lvl2_id, 
                       data = data,
                       correlation = corAR1(),
                  control = ctrl_config,
                  method = 'ML')
  
  # create list with results
  results <- list('baseline' = baseline, 
                  "random_intercept" = random_intercept, 
                  "random_slope" = random_slope,
                  "interaction" = interaction)
  
  
  if (ctrls == 'dem' | ctrls == 'prev'){
    
    # random intercept random slope
    random_slope_ctrl_dem <- lme(fixed = y ~ lvl1_x + lvl2_x + popdens,
                              random = ~ lvl1_x | lvl2_id, 
                          data = data,
                          correlation = corAR1(),
                    control = ctrl_config,
                  method = 'ML')
  
    # cross level interaction
    interaction_ctrl_main_dem <- lme(fixed = y ~ lvl1_x * lvl2_x + popdens,
                             random = ~ lvl1_x | lvl2_id, 
                         data = data,
                         correlation = corAR1(),
                    control = ctrl_config,
                  method = 'ML')
  
    # cross level interaction
    interaction_ctrl_int_dem <- lme(fixed = y ~ lvl1_x * lvl2_x + lvl1_x * popdens,
                             random = ~ lvl1_x | lvl2_id, 
                         data = data,
                         correlation = corAR1(),
                    control = ctrl_config,
                  method = 'ML')        
    
    # create list with results
    results <- list('baseline' = baseline, 
                    "random_intercept" = random_intercept, 
                    "random_slope" = random_slope,
                    "interaction" = interaction,
                    "random_slope_ctrl_dem" = random_slope_ctrl_dem,
                    "interaction_ctrl_main_dem" = interaction_ctrl_main_dem,
                    "interaction_ctrl_int_dem" = interaction_ctrl_int_dem)
  }
  
  if (ctrls == 'prev'){
  
    # random intercept random slope
    random_slope_ctrl_prev <- lme(fixed = y ~ lvl1_x + lvl2_x + popdens + rate_day,
                              random = ~ lvl1_x + rate_day | lvl2_id, 
                          data = data,
                          correlation = corAR1(),
                          control = ctrl_config,
                  method = 'ML')  
    
        # cross level interaction
    interaction_ctrl_main_prev <- lme(fixed = y ~ lvl1_x * lvl2_x + popdens + rate_day,
                             random = ~ lvl1_x | lvl2_id, 
                         data = data,
                         correlation = corAR1(),
                    control = ctrl_config,
                  method = 'ML')
  
  
    # cross level interaction
    interaction_ctrl_int_prev<- lme(fixed = y ~ lvl1_x * lvl2_x + lvl1_x * popdens + rate_day,
                             random = ~ lvl1_x + rate_day | lvl2_id, 
                         data = data,
                         correlation = corAR1(),
                          control = ctrl_config,
                  method = 'ML')
  
    # create list with results
    results <- list('baseline' = baseline, 
                    "random_intercept" = random_intercept, 
                    "random_slope" = random_slope,
                    "interaction" = interaction,
                    "random_slope_ctrl_dem" = random_slope_ctrl_dem,
                    "interaction_ctrl_main_dem" = interaction_ctrl_main_dem,
                    "interaction_ctrl_int_dem" = interaction_ctrl_int_dem,                    
                    "random_slope_ctrl_prev" = random_slope_ctrl_prev,
                    "interaction_ctrl_main_prev" = interaction_ctrl_main_prev,
                    "interaction_ctrl_int_prev" = interaction_ctrl_int_prev)
  }
  
  if(ctrls == 'exp'){
    # random intercept random slope
  random_slope_exp <- lme(fixed = y ~ (lvl1_x + I(lvl1_x^2)) + lvl2_x, 
                      random = ~ (lvl1_x + I(lvl1_x^2)) | lvl2_id, 
                        data = data,
                        correlation = corAR1(),
                  control = ctrl_config,
                  method = 'ML')

  # cross level interaction
  interaction_exp <- lme(fixed = y ~ (lvl1_x + I(lvl1_x^2)) * lvl2_x, 
                     random = ~ (lvl1_x + I(lvl1_x^2)) | lvl2_id, 
                       data = data,
                       correlation = corAR1(),
                  control = ctrl_config,
                  method = 'ML')  
  
  
  # create list with results
  results <- list('baseline' = baseline, 
                  "random_intercept" = random_intercept, 
                  "random_slope" = random_slope,
                  "interaction" = interaction,                  
                  "random_slope_exp" = random_slope_exp,
                  "interaction_exp" = interaction_exp)
  }
  
  return(results)
        
}

# extracts table with coefficients and tests statistics
extract_results <- function(models) {
  
  models_summary <- models %>% 
  map(summary) %>% 
  map("tTable") %>% 
  map(as.data.frame) %>% 
  map(round, 10) 
  # %>% map(~ .[str_detect(rownames(.), 'Inter|lvl'),])
  
  return(models_summary)
  
}


# calculates comparison of all models in model list
compare_models <- function(models) {

  mdl_names <- models %>% names()
  
  str = ''
  for (i in mdl_names){
    
    mdl_str <- paste('models$', i, sep = '')
    
    if(i == 'baseline'){
      str <- mdl_str
    }else{
    str <- paste(str, mdl_str, sep=', ')
    }
  }
  
  anova_str <- paste0('anova(', str, ')')
  mdl_comp <- eval(parse(text=anova_str))
  rownames(mdl_comp) = mdl_names
  return(mdl_comp)
}


```

## Remove London Data 
```{r}
# df_uk <- df_uk %>% filter(london == 'country')
# df_uk_socdist <- df_uk_socdist %>% filter(london == 'country')

```



## Rescale Data
```{r}
lvl2_scaled_ut <- df_uk %>% 
  dplyr::select(-time, -frequ, -rate_day, -london) %>% 
  distinct() %>% 
  mutate_at(vars(-ut_area), scale)

lvl1_scaled_ut <- df_uk %>% select(ut_area, time, rate_day) %>% 
  mutate_at(vars(-ut_area, -time), scale)

df_uk_scaled <- plyr::join(lvl1_scaled_ut, lvl2_scaled_ut, by = 'ut_area')

head(df_uk_scaled)
```


```{r}

lvl2_scaled_nuts <- df_uk_socdist %>% 
  dplyr::select(-time, -date, -frequ, -london, 
                -socdist_tiles, -socdist_single_tile, -rate_day) %>% 
  distinct() %>% 
  mutate_at(vars(-nuts3), scale)

lvl1_scaled_nuts <- df_uk_socdist %>% select(nuts3, time, socdist_single_tile, rate_day) %>% 
  mutate_at(vars(-nuts3, -time), scale)

df_uk_socdist_scaled <- plyr::join(lvl1_scaled_nuts, lvl2_scaled_nuts, by = 'nuts3')

head(df_uk_socdist_scaled)

```



## Predict prevalence
### prevalence ~ openness
```{r}

models_o_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_o', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'dem')

extract_results(models_o_covid)

compare_models(models_o_covid)

```

### prevalence ~ conscientiousness
```{r}

models_c_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_c', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'dem')

extract_results(models_c_covid)

compare_models(models_c_covid)


```

### prevalence ~ extraversion
```{r}

models_e_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_e', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'dem')

extract_results(models_e_covid)

compare_models(models_e_covid)


```

### prevalence ~ agreeableness
```{r}

models_a_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_a', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'dem')

extract_results(models_a_covid)

compare_models(models_a_covid)


```

### prevalence ~ neuroticism
```{r}

models_n_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_n', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'dem')

extract_results(models_n_covid)

compare_models(models_n_covid)


```


## Predict social distancing
### social distancing ~ openness
```{r}

models_o_socdist <-run_models(y = 'socdist_single_tile', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_o', 
                         lvl2_id = 'nuts3', 
                         data = df_uk_socdist_scaled,
                         ctrls = 'prev')

extract_results(models_o_socdist)

compare_models(models_o_socdist)

```

### social distancing ~ conscientiousness
```{r}

models_c_socdist <-run_models(y = 'socdist_single_tile', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_c', 
                         lvl2_id = 'nuts3', 
                         data = df_uk_socdist_scaled,
                         ctrls = 'prev')

extract_results(models_c_socdist)

compare_models(models_c_socdist)


```

### social distancing ~ extraversion
```{r}

models_e_socdist <-run_models(y = 'socdist_single_tile', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_e', 
                         lvl2_id = 'nuts3', 
                         data = df_uk_socdist_scaled,
                         ctrls = 'prev')

extract_results(models_e_socdist)

compare_models(models_e_socdist)


```

### social distancing ~ agreeableness
```{r}

models_a_socdist <-run_models(y = 'socdist_single_tile', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_a', 
                         lvl2_id = 'nuts3', 
                         data = df_uk_socdist_scaled,
                         ctrls = 'prev')

extract_results(models_a_socdist)

compare_models(models_a_socdist)


```

### social distancing ~ neuroticism
```{r}

models_n_socdist <-run_models(y = 'socdist_single_tile', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_n', 
                         lvl2_id = 'nuts3', 
                         data = df_uk_socdist_scaled,
                         ctrls = 'prev')

extract_results(models_n_socdist)

compare_models(models_n_socdist)


```


## Explore quadratic trends 

### prevalence ~ openness
```{r}

models_o_covid_exp <-run_models(y = 'rate_day',
                         lvl1_x = 'time',
                         lvl2_x = 'pers_o',
                         lvl2_id = 'ut_area',
                         data = df_uk_scaled,
                         ctrls = 'exp')

extract_results(models_o_covid_exp)

compare_models(models_o_covid_exp)

```


## prevalence ~ conscientiousness
```{r}

models_c_covid_exp <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_c', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'exp')

extract_results(models_c_covid_exp)

compare_models(models_c_covid_exp)

```

### prevalence ~ extraversion
```{r}

models_e_covid_exp <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_e', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'exp')

extract_results(models_e_covid_exp)

compare_models(models_e_covid_exp)

```

### prevalence ~ agreeableness
```{r}

models_a_covid_exp <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_a', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'exp')

extract_results(models_a_covid_exp)

compare_models(models_a_covid_exp)

```

### prevalence ~ neuroticism
```{r}

models_n_covid_exp <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_n', 
                         lvl2_id = 'ut_area', 
                         data = df_uk_scaled,
                         ctrls = 'exp')

extract_results(models_n_covid_exp)

compare_models(models_n_covid_exp)

```

## Create overview table 

### Define function to create overview tables
```{r}

summary_table <- function(models, dv_name, prev=F){

  temp_df_ctrl_main <- NULL
  temp_df_ctrl_int <- NULL
  temp_df_ctrl_int_prev <- NULL
  
  for (i in models){
    results <- i %>% extract_results()
    
    results_ctrl_main <- results$interaction_ctrl_main_dem['lvl1_x:lvl2_x',]
    temp_df_ctrl_main <- temp_df_ctrl_main %>% rbind(results_ctrl_main)
    
    results_ctrl_int <- results$interaction_ctrl_int_dem['lvl1_x:lvl2_x',]
    temp_df_ctrl_int <- temp_df_ctrl_int %>% rbind(results_ctrl_int)
    
    if(prev){
      results_ctrl_int_prev <- results$interaction_ctrl_int_prev['lvl1_x:lvl2_x',]
      temp_df_ctrl_int_prev <- temp_df_ctrl_int_prev %>% rbind(results_ctrl_int_prev)
    }
        
  }
  
  names_ctrl_main <- paste0(dv_name, '~', c('o', 'c', 'e', 'a', 'n'), '*time', '_crtl_popdens')
  rownames(temp_df_ctrl_main) <- names_ctrl_main

  names_ctrl_int <- paste0(dv_name, '~', c('o', 'c', 'e', 'a', 'n'), '*time', '_crtl_popdens*time')
  rownames(temp_df_ctrl_int) <- names_ctrl_int

  if(prev){
    names_ctrl_int_prev <- paste0(dv_name, '~', c('o', 'c', 'e', 'a', 'n'), '*time', '_crtl_popdens*time_prev')
    rownames(temp_df_ctrl_int_prev) <- names_ctrl_int_prev
    
    sum_tab <- rbind(temp_df_ctrl_main, temp_df_ctrl_int, temp_df_ctrl_int_prev) %>% round(4)
  }else{
    sum_tab <- rbind(temp_df_ctrl_main, temp_df_ctrl_int) %>% round(4)
  }


  
  return(sum_tab)

} 

```

### Create overview tables
```{r}
# prevalence
models_prev <- list(models_o_covid, 
                    models_c_covid, 
                    models_e_covid, 
                    models_a_covid, 
                    models_n_covid)

sum_tab_prev <- summary_table(models_prev, dv_name = 'prev')

write.table(sum_tab_prev, quote=F)

# social distancing
models_socdist <- list(models_o_socdist, 
                       models_c_socdist, 
                       models_e_socdist, 
                       models_a_socdist, 
                       models_n_socdist)

sum_tab_socdist <- summary_table(models_socdist, dv_name = 'socdist', prev=T)

write.table(sum_tab_socdist, quote=F)



```



# Conditional random forest analysis 

### Extract slopes prevalence
```{r}

# slope prevalence
df_uk_slope_prev <- df_uk_scaled %>% split(.$ut_area) %>% 
  map(~ lm(rate_day ~ time, data = .)) %>%
  map(coef) %>% 
  map_dbl('time') %>% 
  as.data.frame() %>% 
  rownames_to_column('ut_area') %>% 
  rename(slope_prev = '.')

# merge with control variables 
df_uk_slope_prev <- df_uk_scaled %>% select(-time, -rate_day) %>%
  distinct() %>% 
  inner_join(df_uk_slope_prev, by = 'ut_area') %>%
  drop_na()

head(df_uk_slope_prev)

```


### Extract slopes social distancing
```{r}

# slope socdist
df_uk_slope_socdist <- df_uk_socdist_scaled %>% split(.$nuts3) %>%
  map(~ lm(socdist_single_tile ~ time, data = .)) %>%
  map(coef) %>%
  map_dbl('time') %>%
  as.data.frame() %>%
  rownames_to_column('nuts3') %>%
  rename(slope_socdist = '.')

# merge with control variables 
df_uk_slope_socdist <- df_uk_socdist_scaled %>% 
  select(-time, -date, -socdist_tiles, -socdist_single_tile) %>%
  distinct() %>%
  inner_join(df_uk_slope_socdist, by = 'nuts3') %>%
  drop_na()

head(df_uk_slope_socdist)

```

### Explore distribution of slopes
```{r}
df_uk_slope_prev %>% ggplot(aes(slope_prev)) + geom_histogram(bins = 100)

df_uk_slope_socdist %>% ggplot(aes(slope_socdist)) + geom_histogram(bins = 100)

```

```{r}
df_uk_slope_prev
```


# CRF prevalence ~ openness
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_o_fit_prev <- cforest(slope_prev ~ pers_o + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_prev[-1], 
                         controls = ctrls)

crf_o_varimp_prev <- varimp(crf_o_fit_prev, nperm = 1)
crf_o_varimp_cond_prev <- varimp(crf_o_fit_prev, conditional = T, nperm = 1)

crf_o_varimp_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_o_varimp_cond_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90))

```

# CRF prevalence ~ conscientiousness
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_c_fit_prev <- cforest(slope_prev ~ pers_c + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_prev[-1], 
                         controls = ctrls)

crf_c_varimp_prev <- varimp(crf_c_fit_prev, nperm = 1)
crf_c_varimp_cond_prev <- varimp(crf_c_fit_prev, conditional = T, nperm = 1)

crf_c_varimp_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_c_varimp_cond_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```


# CRF prevalence ~ extraversion
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_e_fit_prev <- cforest(slope_prev ~ pers_e + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_prev[-1], 
                         controls = ctrls)

crf_e_varimp_prev <- varimp(crf_e_fit_prev, nperm = 1)
crf_e_varimp_cond_prev <- varimp(crf_e_fit_prev, conditional = T, nperm = 1)

crf_e_varimp_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_e_varimp_cond_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```


# CRF prevalence ~ agreeableness
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_a_fit_prev <- cforest(slope_prev ~ pers_a + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_prev[-1], 
                         controls = ctrls)

crf_a_varimp_prev <- varimp(crf_a_fit_prev, nperm = 1)
crf_a_varimp_cond_prev <- varimp(crf_a_fit_prev, conditional = T, nperm = 1)

crf_a_varimp_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_a_varimp_cond_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```


# CRF prevalence ~ neuroticism
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_n_fit_prev <- cforest(slope_prev ~ pers_n + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_prev[-1], 
                         controls = ctrls)

crf_n_varimp_prev <- varimp(crf_n_fit_prev, nperm = 1)
crf_n_varimp_cond_prev <- varimp(crf_n_fit_prev, conditional = T, nperm = 1)

crf_n_varimp_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_n_varimp_cond_prev %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```


# CRF social distancing ~ openness
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_o_fit_socdist <- cforest(slope_socdist ~ pers_o + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_socdist[-1], 
                         controls = ctrls)

crf_o_varimp_socdist <- varimp(crf_o_fit_socdist, nperm = 1)
crf_o_varimp_cond_socdist <- varimp(crf_o_fit_socdist, conditional = T, nperm = 1)

crf_o_varimp_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_o_varimp_cond_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```

# CRF social distancing ~ conscientiousness
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_c_fit_socdist <- cforest(slope_socdist ~ pers_c + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_socdist[-1], 
                         controls = ctrls)

crf_c_varimp_socdist <- varimp(crf_c_fit_socdist, nperm = 1)
crf_c_varimp_cond_socdist <- varimp(crf_c_fit_socdist, conditional = T, nperm = 1)

crf_c_varimp_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_c_varimp_cond_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```

# CRF social distancing ~ extraversion
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_e_fit_socdist <- cforest(slope_socdist ~ pers_e + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_socdist[-1], 
                         controls = ctrls)

crf_e_varimp_socdist <- varimp(crf_e_fit_socdist, nperm = 1)
crf_e_varimp_cond_socdist <- varimp(crf_e_fit_socdist, conditional = T, nperm = 1)

crf_e_varimp_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_e_varimp_cond_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```

# CRF social distancing ~ agreeableness
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_a_fit_socdist <- cforest(slope_socdist ~ pers_a + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_socdist[-1], 
                         controls = ctrls)

crf_a_varimp_socdist <- varimp(crf_a_fit_socdist, nperm = 1)
crf_a_varimp_cond_socdist <- varimp(crf_a_fit_socdist, conditional = T, nperm = 1)

crf_a_varimp_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_a_varimp_cond_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```


# CRF social distancing ~ neuroticism
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_n_fit_socdist <- cforest(slope_socdist ~ pers_n + airport_dist + males +
                          popdens + manufacturing + tourism +
                          health + academic + medinc + medage + conservative, 
                         df_uk_slope_socdist[-1], 
                         controls = ctrls)

crf_n_varimp_socdist <- varimp(crf_n_fit_socdist, nperm = 1)
crf_n_varimp_cond_socdist <- varimp(crf_n_fit_socdist, conditional = T, nperm = 1)

crf_n_varimp_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_n_varimp_cond_socdist %>% as.data.frame() %>% rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

```
