---
title: "Supplementary Information"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: true
    toc_depth: 2

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
knitr::opts_chunk$set(dev="png")
#knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_knit$set(root.dir = normalizePath('../Data/GER'))
options(tibble.print_max = 25)

library(knitr)
library(kableExtra)
library(lmerTest)
library(nlme)
library(psych)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(party)
library(survminer)
library(survival)
library(survMisc)
library(changepoint)
library(specr)
library(DT)
library(stargazer)


source('COVID19_functions.R')
```


```{r, echo=FALSE}
load("../Data/US/US_spec_results.RData")
load("../Data/GER/GER_spec_results.RData")

```

```{r, echo=FALSE}
# select relevant output columns 
select_cols <- function(df){
  df %>% select(controls, estimate, std.error, statistic, p.value, conf.low, conf.high, fit_r.squared)
}


# calculate summary statistics
calc_summary <- function(df){
  
  dft <- df %>% select(estimate:fit_nobs)
  dft <- dft %>% mutate(significant = as.numeric(p.value<0.05),
                        positive = as.numeric(statistic>0), 
                        negative = as.numeric(statistic<0), 
                        significant_positive = as.numeric(p.value<0.05 & statistic>0),
                        significant_negative = as.numeric(p.value<0.05 & statistic<0))
  
  mean_temp <- dft %>% map_if(is.numeric, mean, .else=NULL) %>% as.data.frame()
  sd_temp <- dft %>% map_if(is.numeric, sd, .else=NULL) %>% as.data.frame()
  
  df_temp <- rbind(mean_temp, sd_temp)
  row.names(df_temp) <- c('mean', 'sd')
  
  df_temp <- df_temp %>% select(estimate, std.error, statistic, 
                     p.value, conf.low, conf.high, fit_r.squared, significant,
                     positive, negative, significant_positive, significant_negative
                     ) %>% rename (b = estimate, se = std.error, t = statistic, p = p.value,
          `ci-` = conf.low, `ci+`  = conf.high, `r^2` = fit_r.squared, sig = significant, 
          `b+` = positive, `b-`=negative, `sig+`=significant_positive,
          `sig-`= significant_negative) %>% mutate_all(round, 3)
  
  row.names(df_temp) <- c('mean', 'sd')

   # 
  
  df_temp %>% rownames_to_column(var='summary') %>% 
    datatable(rownames = FALSE)
}
  
  
# adapted from specr package code
format_results <- function(df, var, null = 0, desc = FALSE) {

  # rank specs
  if (isFALSE(desc)) {
    df <- df %>%
      dplyr::arrange(!! var)
  } else {
    df <- df %>%
      dplyr::arrange(desc(!! var))
  }

  # create rank variable and color significance
  df <- df %>%
    dplyr::mutate(specifications = 1:nrow(df),
                  color = case_when(conf.low > null ~ "#377eb8",
                                    conf.high < null ~ "#e41a1c",
                                    TRUE ~ "darkgrey"))
  return(df)
}


# define function to plot single specification curve
plot_curves <- function(results, hr=F){

  if(hr==F){
    
    results %>%
    format_results(var = .$estimate, null = 0, desc = F) %>%
    ggplot(aes(x = specifications,
               y = estimate,
               ymin = conf.low,
               ymax = conf.high,
               color = color)) +
    geom_point(aes(color = color),
               size = 1) +
    theme_minimal() +
    scale_color_identity() +
    theme(strip.text = element_blank(),
          axis.line = element_line("black", size = .5),
          legend.position = "none",
          panel.spacing = unit(.75, "lines"),
          axis.text = element_text(colour = "black")) +
    labs(x = "") +
      geom_pointrange(alpha = 0.05,
                      size = .6,
                      fatten = 1) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
    labs(x = "", y = "standarized effect size") + 
      theme(panel.border = element_blank(), panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(), 
            axis.line = element_line(colour = "black"))
    
  }else{
    
    results %>%
    format_results(var = .$estimate, null = 1, desc = F) %>%
    ggplot(aes(x = specifications,
               y = estimate,
               ymin = conf.low,
               ymax = conf.high,
               color = color)) +
    geom_point(aes(color = color),
               size = 1) +
    theme_minimal() +
    scale_color_identity() +
    theme(strip.text = element_blank(),
          axis.line = element_line("black", size = .5),
          legend.position = "none",
          panel.spacing = unit(.75, "lines"),
          axis.text = element_text(colour = "black")) +
    labs(x = "") +
      geom_pointrange(alpha = 0.05,
                      size = .6,
                      fatten = 1) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
    labs(x = "", y = "effect on hazard ratio") + 
      theme(panel.border = element_blank(), panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(), 
      axis.line = element_line(colour = "black"))
    }
  
}

interactive_table <- function(df){
  

  df %>% select_cols() %>% 
  mutate_if(is.numeric, round, 3) %>%
  rename (control_spec = controls, b = estimate, se = std.error, t = statistic, 
          p = p.value, `ci-` = conf.low, `ci+`  = conf.high, `r^2` = fit_r.squared)%>% 
    mutate(order = row_number())%>% select(order, everything()) %>%
  datatable(rownames = FALSE,
    extensions = list('Buttons' = NULL),
    options = list(columnDefs = list(list(targets = 1, 
                                          render = JS(
      "function(data, type, row, meta) {","return type === 'display' && data.length > 6 ?",
      "'<span title=\"' + data + '\">' + data.substr(0, 40) + '...</span>' : data;","}"))),  
      dom = 'Bfrtip',
      buttons = c('csv'), autoWidth = TRUE,
                       columnDefs = list(list(width = '10px', targets = list(0)))),
    callback = JS('table.page(0).draw(false);'))
  
}


```


# Literature and Data Sources
## Overview of Relationships Between Personality Traits and COVID-19-related Compliance Behaviors
| <br>

Personality Trait | Outcome and Directionality of Association                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        | Reference                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          |
| -------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- | ---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Openness                | Social distancing (+)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               | [AL-Omiri et al., 2021](https://www.frontiersin.org/articles/10.3389/fpsyt.2021.608730/full)<sup>1</sup>;  [Aschwanden et al., 2020](https://onlinelibrary.wiley.com/doi/pdfdirect/10.1002/per.2281)<sup>2</sup>; [Bogg & Milad, 2020](https://psyarxiv.com/yc2gq/)<sup>3</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>; [Ludeke et al., 2021](https://doi.org/10.1016/j.paid.2021.110828)<sup>5</sup>                                                                                                                                                                                                                                                                       |
|| Sheltering-in-place (+)    | [Chan et al., 2020](https://journals.sagepub.com/doi/pdf/10.1177/1948550620952572)<sup>6</sup>; [Götz et al., 2020](https://psycnet.apa.org/fulltext/2020-76208-001.html)<sup>7</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            |
|| Overall compliance (+)     | [Airaksinen et al., 2021](https://psyarxiv.com/rvbjf/)<sup>8</sup>;  [Clark et al., 2020](https://doi.org/10.1016/j.glt.2020.06.003)<sup>9</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>; [Nofal et al., 2020](https://doi.org/10.1371/journal.%20pone.0240396)<sup>10</sup>;  [Qian & Yahara, 2020](https://doi.org/10.1371/journal.pone.0235883)<sup>11</sup>; [Rammstedt et al., 2021](https://journals.sagepub.com/doi/10.1177/0890207021996970)<sup>12</sup>;[Wright & Fancourt, 2020](https://www.medrxiv.org/content/10.1101/2020.11.10.20228403v1)<sup>13</sup>; [Zettler et al., 2021](https://journals.sagepub.com/doi/10.1177/19485506211001680)<sup>14</sup>                                                                                                                                                                                                                                                                                                     |
| Conscientiousness       | Social distancing (+)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              | [Abdelrahman, 2020](https://link.springer.com/article/10.1007/s11469-020-00352-7)<sup>15</sup>; [AL-Omiri et al., 2021](https://www.frontiersin.org/articles/10.3389/fpsyt.2021.608730/full)<sup>1</sup>; [Aschwanden et al., 2020](https://onlinelibrary.wiley.com/doi/pdfdirect/10.1002/per.2281)<sup>2</sup>; [Blagov, 2020](https://journals.sagepub.com/doi/full/10.1177/1948550620936439)<sup>1</sup>; [Bogg & Milad, 2020](https://psyarxiv.com/yc2gq/)<sup>2</sup>; [Carvalho et al., 2020](https://pubmed.ncbi.nlm.nih.gov/32294713/)<sup>16</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>;  [Ludeke et al., 2021](https://doi.org/10.1016/j.paid.2021.110828)<sup>5</sup> |
|| Sheltering-in-place (+)    | [Götz et al., 2020](https://psycnet.apa.org/fulltext/2020-76208-001.html)<sup>7</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            |
|| Overall compliance (+)     | [Airaksinen et al., 2021](https://psyarxiv.com/rvbjf/)<sup>8</sup>;  [Brouard et al., 2020](https://www.cambridge.org/core/journals/canadian-journal-of-political-science-revue-canadienne-de-science-politique/article/sociodemographic-and-psychological-correlates-of-compliance-with-the-covid19-public-health-measures-in-france/3704E20ABAF59BCD6842BAA307540BFE)<sup>18</sup>; [Clark et al., 2020](https://doi.org/10.1016/j.glt.2020.06.003)<sup>1</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>; [Krupíc et al., 2021](https://doi.org/10.1016/j.paid.2021.110913)<sup>19</sup>; [Nofal et al., 2020](https://doi.org/10.1371/journal.%20pone.0240396)<sup>10</sup>;  [Qian & Yahara, 2020](https://doi.org/10.1371/journal.pone.0235883)<sup>11</sup>; [Wright & Fancourt, 2020](https://www.medrxiv.org/content/10.1101/2020.11.10.20228403v1)<sup>13</sup>; [Zettler et al., 2021](https://journals.sagepub.com/doi/10.1177/19485506211001680)<sup>14</sup>  |
| Extraversion            | Social distancing (-)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              | [Blagov, 2020](https://journals.sagepub.com/doi/full/10.1177/1948550620936439)<sup>16</sup>; [Carvalho et al., 2020](https://pubmed.ncbi.nlm.nih.gov/32294713/)<sup>17</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>; [Ludeke et al., 2021](https://doi.org/10.1016/j.paid.2021.110828)<sup>5</sup>                                                                                                                                                                                                                                                                                                                                                                        |
|| Social distancing (+)      | [AL-Omiri et al., 2021](https://www.frontiersin.org/articles/10.3389/fpsyt.2021.608730/full)<sup>1</sup>;  [Shook et al., 2020](https://journals.plos.org/plosone/article/file?id=10.1371/journal.pone.0238015&type=printable)<sup>20</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               |
|| Sheltering-in-place (-)    | [Chan et al., 2020](https://journals.sagepub.com/doi/pdf/10.1177/1948550620952572)<sup>6</sup>; [Götz et al., 2020](https://psycnet.apa.org/fulltext/2020-76208-001.html)<sup>7</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            |
|| Overall compliance (+)     | [Qian & Yahara, 2020](https://doi.org/10.1371/journal.pone.0235883)<sup>11</sup>; [Rammstedt et al., 2021](https://journals.sagepub.com/doi/10.1177/0890207021996970)<sup>12</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             |
|| Overall compliance (-)     | [Brouard et al., 2020](https://www.cambridge.org/core/journals/canadian-journal-of-political-science-revue-canadienne-de-science-politique/article/sociodemographic-and-psychological-correlates-of-compliance-with-the-covid19-public-health-measures-in-france/3704E20ABAF59BCD6842BAA307540BFE)<sup>18</sup> ; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>;  [Nofal et al., 2020](https://doi.org/10.1371/journal.%20pone.0240396)<sup>10</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        |
| Agreeableness           | Social distancing (+)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              | [Aschwanden et al., 2020](https://onlinelibrary.wiley.com/doi/pdfdirect/10.1002/per.2281)<sup>2</sup>; [Blagov, 2020](https://journals.sagepub.com/doi/full/10.1177/1948550620936439)<sup>16</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>;  [Ludeke et al., 2021](https://doi.org/10.1016/j.paid.2021.110828)<sup>5</sup>                                                                                                                                                                                                                                                                                                                                             |
|| Social distancing (-)     | [Abdelrahman, 2020](https://link.springer.com/article/10.1007/s11469-020-00352-7)<sup>15</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    |
|| Sheltering-in-place (+)    | [Götz et al., 2020](https://psycnet.apa.org/fulltext/2020-76208-001.html)<sup>7</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            |
|| Overall compliance (+)     | [Asselmann et al., 2020](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0242904)<sup>21</sup>; [Clark et al., 2020](https://doi.org/10.1016/j.glt.2020.06.003)<sup>9</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>; [Krupíc et al., 2021](https://doi.org/10.1016/j.paid.2021.110913)<sup>19</sup>;  [Nofal et al., 2020](https://doi.org/10.1371/journal.%20pone.0240396)<sup>10</sup>; [Qian & Yahara, 2020](https://doi.org/10.1371/journal.pone.0235883)<sup>11</sup>; [Rammstedt et al., 2021](https://journals.sagepub.com/doi/10.1177/0890207021996970)<sup>12</sup>; [Wright & Fancourt, 2020](https://www.medrxiv.org/content/10.1101/2020.11.10.20228403v1)<sup>13</sup>; [Zajenkowski et al., 2020](https://www.sciencedirect.com/science/article/pii/S0191886920303883)<sup>22</sup>; [Zettler et al., 2021](https://journals.sagepub.com/doi/10.1177/19485506211001680)<sup>14</sup>                                                                     |
| Neuroticism             | Social distancing (+)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               | [Abdelrahman, 2020](https://link.springer.com/article/10.1007/s11469-020-00352-7)<sup>15</sup>; [Blagov, 2020](https://journals.sagepub.com/doi/full/10.1177/1948550620936439)<sup>16</sup>; [Bogg & Milad, 2020](https://psyarxiv.com/yc2gq/)<sup>3</sup>; [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>;  [Ludeke et al., 2021](https://doi.org/10.1016/j.paid.2021.110828)<sup>5</sup>                                                                                                                                                                                                                                                                                     |
|| Sheltering-in-place (+)    | [Chan et al., 2020](https://journals.sagepub.com/doi/pdf/10.1177/1948550620952572)<sup>6</sup>; [Götz et al., 2020](https://psycnet.apa.org/fulltext/2020-76208-001.html)<sup>7</sup>                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            |
|| Overall compliance (+)     | [Airaksinen et al., 2021](https://psyarxiv.com/rvbjf/)<sup>8</sup>;  [Han, 2021](https://doi.org/10.1016/j.paid.2021.110787)<sup>4</sup>;  [Qian & Yahara, 2020](https://doi.org/10.1371/journal.pone.0235883)<sup>11</sup>; [Rammstedt et al., 2021](https://journals.sagepub.com/doi/10.1177/0890207021996970)<sup>12</sup>; [Wright & Fancourt, 2020](https://www.medrxiv.org/content/10.1101/2020.11.10.20228403v1)<sup>13</sup>



## Operationalizations and Sources of Control Variables

| Variables                       | United States                                                                                      | Germany                           | Name in Markdown                                                                        |
| ----------------------------------  | -------------------------------------------------------|------------------------------------------- | --------------------------- |
| _Socio-demographic controls_    |                                                                                                    |                                                                                     |
|      Age                        | Median Age in 2018[<sup>23</sup>](https://www.census.gov)                                                                    | Average Age in 2017[<sup>24</sup>](https://www.inkar.de)                                                    | age|
|      Gender                     | Share of males (%) in population in 2018[<sup>23</sup>](https://www.census.gov)                                             | Share of males (%) in population in 2017[<sup>24</sup>](https://www.inkar.de)                               | male|
|      Political orientation      | Average share of votes for republican party (%) in 2008 - 2016 presidential elections[<sup>23</sup>](https://www.census.gov)    | Share of votes for AfD party (%) in 2017 parliamentary election[<sup>24</sup>](https://www.inkar.de)        | conservative |
| _Socio-economic controls_       |                                                                                                    |                                                                                     |
|      Educational attainment     | Share of population 25 years or older with tertiary education (%) in 2018[<sup>23</sup>](https://www.census.gov)             | Share of employees with tertiary education (%) in 2017[<sup>24</sup>](https://www.inkar.de)                 | academics|
|      Income                     | Median monthly household income in USD in 2018[<sup>23</sup>](https://www.census.gov)                                        | Median monthly income of employees in EUR in 2017[<sup>24</sup>](https://www.inkar.de)                      | medinc|
|      Industrial composition     | Share of employees in industry sector (%) in 2018[<sup>23</sup>](https://www.census.gov)                                     | Share of employees in industry sector (%) in 2017[<sup>24</sup>](https://www.inkar.de)                      | manufact|
| _Pandemic-related controls_     |                                                                                                    |                                                                                     |
|      International connectivity | Distance to nearest major airport in kilometers from centroid of county (own calculation for 2020) | Average travel time by car to nearest major airport in minutes in 2018[<sup>24</sup>](https://www.inkar.de) | airport_dist|
|      Tourism                    | Share of employed population in food and accommodation services sector (%) in 2018[<sup>23</sup>](https://www.census.gov)    | Hotel beds per 1000 inhabitants in 2017[<sup>24</sup>](https://www.inkar.de)                                | tourism |
|      Health care                | Primary care physicians per 1000 inhabitants in 2018[<sup>23</sup>](https://www.census.gov)                                  | Hospital beds per 1000 inhabitants in 2017[<sup>24</sup>](https://www.inkar.de)                             | healthcare |
|      Population density         | Inhabitants per square mile in 2018[<sup>23</sup>](https://www.census.gov)                                                   | Inhabitants per square mile in 2017[<sup>24</sup>](https://www.inkar.de)                                    | popdens |
|      Temperature                | Average monthly temperature in °F[<sup>25</sup>](https://www.ncei.noaa.gov/pub/data/)                                                                | Average monthly temperature in °C[<sup>26</sup>](https://cdc.dwd.de/portal/)                         | temp|
|_COVID-19_                       |                                                                                                    |                                                                                     |
|      Onset                      | Derived from prevalence data                                                                       | Derived from prevalence data                                                        | onset_prev
|      Slope                      | Derived from prevalence data                                                                       | Derived from prevalence data                                                        | slope_prev

# Descriptive Statistics
## Means and Standard Deviations
### Means and Standard Deviations (US)
```{r, echo=FALSE}
df_us_all <-  read.csv("../Data/US/us_all_variables.csv")

us_means <- df_us_all %>% 
  select(pers_o:pers_n, airport_dist:temp, onset_prev:mean_diff_socdist_2) %>% 
  summarise_all(mean)

us_sd <- df_us_all %>% select(-county_fips) %>% summarise_all(sd)

desc_us <- rbind(us_means, us_sd) %>% t() %>% round(3) %>% as.data.frame() %>%
  rownames_to_column() %>% rename(mean=V1, sd=V2, variable = rowname)

desc_us %>% mutate(order = row_number())%>% select(order, everything()) %>% datatable(rownames = FALSE, 
                       options = list(autoWidth = TRUE,
                       columnDefs = list(list(width = '10px', targets = list(0)))))
```

Note. N = 2366 counties.

### Means and Standard Deviations (GER)
```{r, echo=FALSE}
df_ger_all <-  read.csv("../Data/GER/ger_all_variables.csv")
ger_means <- df_ger_all %>% select(-kreis, -latitude, -longitude) %>% summarise_all(mean)
ger_sd <- df_ger_all %>% select(-kreis, -latitude, -longitude) %>% summarise_all(sd)

desc_ger <- rbind(ger_means, ger_sd) %>% t() %>% round(3) %>% as.data.frame() %>%
  rownames_to_column() %>% rename(mean=V1, sd=V2, variable = rowname)

desc_ger %>% mutate(order = row_number())%>% select(order, everything()) %>% datatable(rownames = FALSE, 
                       options = list(autoWidth = TRUE,
                       columnDefs = list(list(width = '10px', targets = list(0)))))
```

Note. N = 379 administrative districts (Kreise).

## Distributions of COVID-19 and Social Distancing Metrics
### Distributions of COVID-19 Onset Dates and Growth Rates (US)
```{r, echo=FALSE}
tto <- df_us_all %>% filter(onset_prev<86) %>%
  ggplot(aes(x=onset_prev+21)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - COVID-19 Onset') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Onset Day')
  
soa <- df_us_all %>% 
  ggplot(aes(x=slope_prev)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - COVID-19 Growth Rates') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Standardized growth rates')

figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of COVID-19 onsets (case rate exceeding 1/10,000, day of the year 2020) and linearized COVID-19 growth rates. Growth rates were calculated by extracting the slopes of linear regression models fitted separately for each region, such that each slope captures the region’s active case rate as a function of time. To account for the exponential nature of the growth curves, active case rates were log-transformed prior to the analyses.


### Distributions of COVID-19 Case Rates in April and September (US)
```{r, echo=FALSE}

tto <- df_us_all %>% 
  ggplot(aes(x=case_rate_0415)) + 
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Case Rates') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Cases Per 1000 Inhabitants')
  
soa <- df_us_all %>%
  ggplot(aes(x=case_rate_0930)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Case Rates') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Cases Per 1000 Inhabitants')


figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of cumulative COVID-19 case rates reported on April 15 and September 30, 2020. 


### Distributions of COVID-19 Death Rates in April and September (US)
```{r, echo=FALSE}

tto <- df_us_all %>% 
  ggplot(aes(x=death_rate_0415)) + 
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Death Rates') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')
  
soa <- df_us_all %>%
  ggplot(aes(x=death_rate_0930)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Death Rates') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')


figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of cumulative COVID-19 death rates reported on April 15 and September 30, 2020. 


### Distributions of Social Distancing Metrics (US)
```{r, echo=FALSE}

tto <- df_us_all %>% 
  ggplot(aes(x=cpt_day_socdist_2)) + 
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Time to Adoption') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')
  
soa <- df_us_all %>%
  ggplot(aes(x=mean_diff_socdist_2)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Adjustment Level') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')


figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of social distancing adoption times (i.e., previously determined change points in the time series) and strength of adjustment (i.e., the magnitude of the reduction in mobility compared to a pre-COVID baseline in February 2020). 


### Distributions of COVID-19 Onset Dates and Growth Rates (GER)
```{r, echo=FALSE}
tto <- df_ger_all %>% filter(onset_prev<86) %>%
  ggplot(aes(x=onset_prev)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - COVID-19 Onset') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Onset Day')
  
soa <- df_ger_all %>% 
  ggplot(aes(x=slope_prev)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - COVID-19 Growth Rates') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Standardized growth rates')

figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of COVID-19 onsets (case rate exceeding 1/10,000, day of the year 2020) and linearized COVID-19 growth rates. Growth rates were calculated by extracting the slopes of linear regression models fitted separately for each region, such that each slope captures the region’s active case rate as a function of time. To account for the exponential nature of the growth curves, active case rates were log-transformed prior to the analyses.


### Distributions of COVID-19 Case Rates in March and September (GER)
```{r, echo=FALSE}

tto <- df_ger_all %>% 
  ggplot(aes(x=case_rate_0331)) + 
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Case Rates') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Cases Per 1000 Inhabitants')
  
soa <- df_ger_all %>%
  ggplot(aes(x=case_rate_0930)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Case Rates') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Cases Per 1000 Inhabitants')


figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of cumulative COVID-19 case rates reported on March 31 and September 30, 2020. 

### Distributions of COVID-19 Death Rates in March and September (GER)
```{r, echo=FALSE}

tto <- df_ger_all %>% 
  ggplot(aes(x=death_rate_0331)) + 
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Death Rates') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')
  
soa <- df_ger_all %>%
  ggplot(aes(x=death_rate_0930)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Cumulative Death Rates') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')


figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of cumulative COVID-19 death rates reported on March 31 and September 30, 2020. 


### Distributions of Social Distancing Metrics (GER)
```{r, echo=FALSE}

tto <- df_ger_all %>% 
  ggplot(aes(x=cpt_day_socdist_2)) + 
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Time to Adoption') + 
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')
  
soa <- df_ger_all %>%
  ggplot(aes(x=mean_diff_socdist_2)) +
  geom_histogram(bins=15) +
  theme_light() +
  ggtitle('Distribution - Adjustment Level') +
  theme(plot.title = element_text(size=11)) +
  ylab('Absolute frequency') +
  xlab('Deaths Per 1000 Inhabitants')


figure <- ggarrange(tto, soa,
                    labels = c("", ""),
                    ncol = 2, nrow = 1)
figure
```

Note: Distributions of social distancing adoption times (i.e., previously determined change points in the time series) and strength of adjustment (i.e., the magnitude of the reduction in mobility compared to a pre-COVID baseline in February 2020). 


## Correlations
### Pearson Correlations (US)
```{r, echo=FALSE}

cols <- c("pers_o", "pers_c", "pers_e", "pers_a", "pers_n", "academics","conservative", "healthcare", "tourism", "manufact", "airport_dist", "age", "male", "medinc", "popdens", "temp", "onset_prev", "slope_prev", "slope_prev_var", "case_rate_0415", "death_rate_0415", "case_rate_0930","death_rate_0930", "cpt_day_socdist_2", "mean_diff_socdist_2")


df_us_all <-  read.csv("../Data/US/us_all_variables.csv")
df_us_all %>% select(-county_fips) %>% cor() %>% round(3) %>% as.data.frame() %>% cbind(cols) %>% rename(variables = cols) %>% mutate(order = row_number())%>% select(c('order', 'variables', cols)) %>% datatable(rownames = FALSE, options = list(scrollX = TRUE, autoWidth = TRUE,
                       columnDefs = list(list(width = '10px', targets = list(0)))))
```

Note. N = 379 counties. The correlations for Covid-19 onsets and social distancing adoption time are based on raw dates such that earlier dates are represented as smaller numbers. Hence, these correlations show the opposite sign compared to the coefficients in the Cox proportional hazard models, where onset and adoption time are represented as hazard ratios such that earlier dates are represented as larger numbers. 



### Pearson Correlations (GER)
```{r, echo=FALSE}
cols <- c("pers_o", "pers_c", "pers_e", "pers_a", "pers_n", "academics","conservative", "healthcare", "tourism", "manufact", "airport_dist", "age", "male", "medinc", "popdens", "temp", "onset_prev", "slope_prev", "slope_prev_var", "case_rate_0331", "death_rate_0331", "case_rate_0930","death_rate_0930", "cpt_day_socdist_2", "mean_diff_socdist_2")


df_ger_all <-  read.csv("../Data/GER/ger_all_variables.csv")
df_ger_all %>% select(-kreis, -latitude, -longitude) %>% cor() %>% round(3) %>% as.data.frame() %>% cbind(cols) %>% rename(variables = cols) %>% mutate(order = row_number())%>% select(c('order', 'variables', cols)) %>% datatable(rownames = FALSE, options = list(scrollX = TRUE, autoWidth = TRUE,
                       columnDefs = list(list(width = '10px', targets = list(0)))))

```

Note. N = 379 administrative districts (Kreise). The correlations for Covid-19 onsets and social distancing adoption time are based on raw dates such that earlier dates are represented as smaller numbers. Hence, these correlations show the opposite signs compared to the coefficients in the Cox proportional hazard models, where onset and adoption time are represented as hazard ratios such that earlier dates are represented as larger numbers.


# Specification Curve Analyses
The following sections include detailed reports of the specification curve analyses presented in the manuscript, as well as robustness checks. For each specification curve analysis we present: 

1) A searchable, sortable overview table showing effect sizes (b denoting hazard ratios in the case of Cox proportional hazard models and standardized regression coefficients in the case of OLS regression models), standard errors (se), test statistics (t), p-values (p), and 95% confidence intervals (ci-, ci+) of the respective personality predictor, as well as determination coefficients of the overall model for all 4096 model specifications (r^2), spanning all combinations of control variables (international connectivity, tourism, health care capabilities, population density, latitude, age, gender, political orientation, educational attainment, income, industrial composition); 

2) A larger, more detailed plot of the corresponding specification curve with effect sizes and 95% confidence intervals, showing significant positive effects in blue and significant negative effects in red; 

3) A table with summary statistics across all 4096 models of each analysis. The table contains mean and standard deviations of effect sizes (b), standard errors (se), test statistics (t), p-values (p), and 95% confidence intervals (ci-, ci+) and determination coefficients (r^2), as well as the proportion of models that showed a significant effect of regional personality (sig), the proportion of models that showed a positive effect of regional personality (b+), the proportion of models that showed a negative effect of regional personality (b-), the proportion of models that showed a significant positive effect of regional personality (sig+), and the proportion of models that showed a significant negative effect of regional personality (sig-).

The data can be downloaded for further analyses using the "csv" button at the top of each table.


## Effects of Regional Personality on COVID-19 Onset
### Regional Opennness and COVID-19 Onset
#### Effects of Openness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_o %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Openness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_o %>% calc_summary()
```

#### Effects of Openness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_o %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Openness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_o %>% calc_summary()
```




### Regional Conscientiousness and COVID-19 Onset
#### Effects of Conscientiousness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_c %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_c %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_c %>% calc_summary()
```




### Regional Extraversion and COVID-19 Onset
#### Effects of Extraversion on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_e %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_e %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_e %>% calc_summary()
```




### Regional Agreeableness and COVID-19 Onset
#### Effects of Agreeableness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_a %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_a %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_a %>% calc_summary()
```




### Regional Neuroticism and COVID-19 Onset
#### Effects of Neuroticism on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_n %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Onset (US)
```{r, echo=FALSE}
results_us$cox_onset_prev_hr$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_n %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Onset (GER)
```{r, echo=FALSE}
results_ger$cox_onset_prev_hr$spec_results_n %>% calc_summary()
```





## Effects of Regional Personality on COVID-19 Growth Rate (Fixed Time Window)
### Regional Opennness and COVID-19 Growth Rate
#### Effects of Openness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_o %>% calc_summary()
```

#### Effects of Openness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_o %>% calc_summary()
```




### Regional Conscientiousness and COVID-19 Growth Rate
#### Effects of Conscientiousness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_c %>% calc_summary()
```




### Regional Extraversion and COVID-19 Growth Rate
#### Effects of Extraversion on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_e %>% calc_summary()
```




### Regional Agreeableness and COVID-19 Growth Rate
#### Effects of Agreeableness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_a %>% calc_summary()
```





### Regional Neuroticism and COVID-19 Growth Rate
#### Effects of Neuroticism on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev$spec_results_n %>% calc_summary()
```




## Effects of Regional Personality on COVID-19 Growth Rate (Variable Time Window)
### Regional Opennness and COVID-19 Growth Rate
#### Effects of Openness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_o %>% calc_summary()
```

#### Effects of Openness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_o %>% calc_summary()
```




### Regional Conscientiousness and COVID-19 Growth Rate
#### Effects of Conscientiousness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_c %>% calc_summary()
```




### Regional Extraversion and COVID-19 Growth Rate
#### Effects of Extraversion on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_e %>% calc_summary()
```




### Regional Agreeableness and COVID-19 Growth Rate
#### Effects of Agreeableness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_a %>% calc_summary()
```




### Regional Neuroticism and COVID-19 Growth Rate
#### Effects of Neuroticism on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Growth Rate (US)
```{r, echo=FALSE}
results_us$lm_slope_prev_var$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Growth Rate (GER)
```{r, echo=FALSE}
results_ger$lm_slope_prev_var$spec_results_n %>% calc_summary()
```





## Effects of Regional Personality on Cumulative COVID-19 Case Rates in March/April
### Regional Opennness and Cumulative COVID-19 Case Rates in March/April
#### Effects of Openness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_o %>% calc_summary()
```

#### Effects of Openness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_o %>% calc_summary()
```




### Regional Conscientiousness and Cumulative COVID-19 Case Rates in March/April
#### Effects of Conscientiousness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_c %>% calc_summary()
```




### Regional Extraversion and Cumulative COVID-19 Case Rates in March/April
#### Effects of Extraversion on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_e %>% calc_summary()
```





### Regional Agreeableness and Cumulative COVID-19 Case Rates in March/April
#### Effects of Agreeableness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_a %>% calc_summary()
```




### Regional Neuroticism and Cumulative COVID-19 Case Rates in March/April
#### Effects of Neuroticism on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on Cumulative COVID-19 Case Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_cases_0415$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on Cumulative COVID-19 Case Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0331$spec_results_n %>% calc_summary()
```




## Effects of Regional Personality on Cumulative COVID-19 Case Rates in September
### Regional Opennness and COVID-19 Case Rates in September
#### Effects of Openness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_o %>% calc_summary()
```

#### Effects of Openness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_o %>% calc_summary()
```




### Regional Conscientiousness and COVID-19 Case Rates in September
#### Effects of Conscientiousness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_c %>% calc_summary()
```




### Regional Extraversion and COVID-19 Case Rates in September
#### Effects of Extraversion on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_e %>% calc_summary()
```




### Regional Agreeableness and COVID-19 Case Rates in September
#### Effects of Agreeableness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_a %>% calc_summary()
```




### Regional Neuroticism and COVID-19 Case Rates in September
#### Effects of Neuroticism on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Case Rates in September (US)
```{r, echo=FALSE}
results_us$lm_cases_0930$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Case Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_cases_0930$spec_results_n %>% calc_summary()
```





## Effects of Regional Personality on Cumulative COVID-19 Death Rates in March/April
### Regional Opennness and Cumulative COVID-19 Death Rates in March/April
#### Effects of Openness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_o %>% calc_summary()
```

#### Effects of Openness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_o %>% calc_summary()
```





### Regional Conscientiousness and Cumulative COVID-19 Death Rates in March/April
#### Effects of Conscientiousness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_c %>% calc_summary()
```




### Regional Extraversion and Cumulative COVID-19 Death Rates in March/April
#### Effects of Extraversion on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_e %>% calc_summary()
```




### Regional Agreeableness and Cumulative COVID-19 Death Rates in March/April
#### Effects of Agreeableness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_a %>% calc_summary()
```





### Regional Neuroticism and Cumulative COVID-19 Death Rates in March/April
#### Effects of Neuroticism on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on Cumulative COVID-19 Death Rates in March/April (US)
```{r, echo=FALSE}
results_us$lm_deaths_0415$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on Cumulative COVID-19 Death Rates in March/April (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0331$spec_results_n %>% calc_summary()
```




## Effects of Regional Personality on Cumulative COVID-19 Death Rates in September
### Regional Opennness and COVID-19 Death Rates in September
#### Effects of Openness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_o %>% calc_summary()
```

#### Effects of Openness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_o %>% calc_summary()
```





### Regional Conscientiousness and COVID-19 Death Rates in September
#### Effects of Conscientiousness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_c %>% calc_summary()
```





### Regional Extraversion and COVID-19 Death Rates in September
#### Effects of Extraversion on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_e %>% calc_summary()
```




### Regional Agreeableness and COVID-19 Death Rates in September
#### Effects of Agreeableness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_a %>% calc_summary()
```




### Regional Neuroticism and COVID-19 Death Rates in September
#### Effects of Neuroticism on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Death Rates in September (US)
```{r, echo=FALSE}
results_us$lm_deaths_0930$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on COVID-19 Death Rates in September (GER)
```{r, echo=FALSE}
results_ger$lm_deaths_0930$spec_results_n %>% calc_summary()
```





## Effects of Regional Personality on Social Distancing Adoption Time
### Regional Opennness and Social Distancing Adoption Time
#### Effects of Openness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_o %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Openness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_o %>% calc_summary()
```

#### Effects of Openness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_o %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Openness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_o %>% calc_summary()
```




### Regional Conscientiousness and Social Distancing Adoption Time
#### Effects of Conscientiousness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_c %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Conscientiousness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_c %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Conscientiousness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_c %>% calc_summary()
```




### Regional Extraversion and Social Distancing Adoption Time
#### Effects of Extraversion on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_e %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Extraversion on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_e %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Extraversion on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_e %>% calc_summary()
```





### Regional Agreeableness and Social Distancing Adoption Time
#### Effects of Agreeableness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_a %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Agreeableness on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_a %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Agreeableness on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_a %>% calc_summary()
```




### Regional Neuroticism and Social Distancing Adoption Time
#### Effects of Neuroticism on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_n %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Neuroticism on Social Distancing Adoption Time (US)
```{r, echo=FALSE}
results_us$cox_onset_socdist_hr$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_n %>% plot_curves(hr = T)
```

#### Summary Statistics of the Effects of Neuroticism on Social Distancing Adoption Time (GER)
```{r, echo=FALSE}
results_ger$cox_onset_socdist_hr$spec_results_n %>% calc_summary()
```



## Effects of Regional Personality on Social Distancing Adjustment Level
### Regional Opennness and Social Distancing Adjustment Level
#### Effects of Openness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_o %>% calc_summary()
```

#### Effects of Openness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_o %>% interactive_table()
```

#### Summary Plot of Effects of Openness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_o %>% plot_curves()
```

#### Summary Statistics of the Effects of Openness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_o %>% calc_summary()
```




### Regional Conscientiousness and Social Distancing Adjustment Level
#### Effects of Conscientiousness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_c %>% calc_summary()
```

#### Effects of Conscientiousness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_c %>% interactive_table()
```

#### Summary Plot of Effects of Conscientiousness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_c %>% plot_curves()
```

#### Summary Statistics of the Effects of Conscientiousness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_c %>% calc_summary()
```





### Regional Extraversion and Social Distancing Adjustment Level
#### Effects of Extraversion on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_e %>% calc_summary()
```

#### Effects of Extraversion on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_e %>% interactive_table()
```

#### Summary Plot of Effects of Extraversion on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_e %>% plot_curves()
```

#### Summary Statistics of the Effects of Extraversion on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_e %>% calc_summary()
```





### Regional Agreeableness and Social Distancing Adjustment Level
#### Effects of Agreeableness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_a %>% calc_summary()
```

#### Effects of Agreeableness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_a %>% interactive_table()
```

#### Summary Plot of Effects of Agreeableness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_a %>% plot_curves()
```

#### Summary Statistics of the Effects of Agreeableness on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_a %>% calc_summary()
```





### Regional Neuroticism and Social Distancing Adjustment Level
#### Effects of Neuroticism on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on Social Distancing Adjustment Level (US)
```{r, echo=FALSE}
results_us$lm_mean_socdist$spec_results_n %>% calc_summary()
```

#### Effects of Neuroticism on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_n %>% interactive_table()
```

#### Summary Plot of Effects of Neuroticism on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_n %>% plot_curves()
```

#### Summary Statistics of the Effects of Neuroticism on Social Distancing Adjustment Level (GER)
```{r, echo=FALSE}
results_ger$lm_mean_socdist$spec_results_n %>% calc_summary()
```


# Additional Analyses 
## Local Social Norms

```{r, include = FALSE}
### Supporting Analyses showing that agreeable and conscientious individuals are more focused on local social norms ###


dat <- read.csv("../Data/US/Covid_Personality_LocalNorms2.csv")
dat$Age <- 2020-dat$YOB
dat$Political_View[dat$Political_View == 6] <- 3  # recode "Not sure" to "neutral"

## Calculate outcomes

# Absolute Local and national similarity in between one's own behavior and that expected of the community
dat$T1_community_similarity <- 0-abs(dat$Follow_localguidelines_community - dat$Follow_localguidelines_self)

# Local and national similarity in between one's own behavior and that expected of the community
dat$T1_community_comparison <- dat$Follow_localguidelines_self - dat$Follow_localguidelines_community 


### Personality and Local Community Compliance

## Does personality predict the extent to which individuals say they follow the guidelines of local leaders?

# Openness
summary(m1 <- lm(Follow_localguidelines_self ~ OP, data = dat))
summary(m2 <- lm(Follow_localguidelines_self ~ OP + Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat))

# Conscientiousness
summary(m3 <- lm(Follow_localguidelines_self ~ CO , data = dat)) 
summary(m4 <- lm(Follow_localguidelines_self ~ CO+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View , data = dat)) 

# Extraversion
summary(m5 <- lm(Follow_localguidelines_self ~ EX, data = dat)) 
summary(m6 <- lm(Follow_localguidelines_self ~ EX+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 

#Agreeableness
summary(m7 <- lm(Follow_localguidelines_self ~ AG, data = dat)) 
summary(m8 <- lm(Follow_localguidelines_self ~ AG+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 

#Emotional Stability
summary(m9 <- lm(Follow_localguidelines_self ~ ES, data = dat)) 
summary(m10 <- lm(Follow_localguidelines_self ~ ES + Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 


## Does personality predict the extent to which individuals do what their local community does?

# Openness
summary(m11 <- lm(T1_community_similarity ~ OP, data = dat))
summary(m12 <- lm(T1_community_similarity ~ OP+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat))

# Conscientiousness
summary(m13 <- lm(T1_community_similarity ~ CO, data = dat))
summary(m14 <- lm(T1_community_similarity ~ CO+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat))

# Extraversion
summary(m15 <- lm(T1_community_similarity ~ EX, data = dat)) 
summary(m16 <- lm(T1_community_similarity ~ EX+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 

#Agreeableness
summary(m17 <- lm(T1_community_similarity ~ AG, data = dat)) 
summary(m18 <- lm(T1_community_similarity ~ AG+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 

#Emotional Stability
summary(m19 <- lm(T1_community_similarity ~ ES, data = dat)) 
summary(m20 <- lm(T1_community_similarity ~ ES+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 


## Does personality predict the extent to which individuals follow the rules more or less than their local community?

# Openness
summary(m21 <- lm(T1_community_comparison ~ OP, data = dat))
summary(m22 <- lm(T1_community_comparison ~ OP+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat))

# Conscientiousness
summary(m23 <- lm(T1_community_comparison ~ CO, data = dat)) 
summary(m24 <- lm(T1_community_comparison ~ CO+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 

# Extraversion
summary(m25 <- lm(T1_community_comparison ~ EX, data = dat)) 
summary(m26 <- lm(T1_community_comparison ~ EX+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 

#Agreeableness
summary(m27 <- lm(T1_community_comparison ~ AG, data = dat)) 
summary(m28 <- lm(T1_community_comparison ~ AG+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 

#Emotional Stability
summary(m29 <- lm(T1_community_comparison ~ ES, data = dat)) 
summary(m30 <- lm(T1_community_comparison ~ ES+ Age + as.factor(Gender) + Education + as.factor(Ethnicity) + as.factor(Employment) + Political_View, data = dat)) 


```


The following analyses provide additional empirical support for the proposition that the effects of regional agreeableness and conscientiousness might, in part, be explained by the stronger adherence of agreeable and conscientious individuals to local community norms (rather than national guidelines). We analysed a sample of 1,038 US Americans who completed a survey between 2020-03-20 and 2020-05-22, the early stage of the COVID-19 pandemic, through the online panel Amazon Mechanical Turk. Among others, the survey assessed the extent to which participants (i) followed the recommendations of local leaders and experts ("adherence-self") and (ii) expected other community member to follow the recommendations of local leaders and experts ("adherence other", both measured on a 7-point scale, ranging from 1 = "Not at all"" to 7 = "Very often"). In addition, participants reported on their socio-demographic characteristics, including age, gender, ethnicity, education, employment status and political ideology. The Big Five personality traits were assessed in another wave of the survey that was collected between 2020-05-07 and 2020-05-11 and can be mapped onto the first survey. They were measures using a well-established short ten-item personality inventory (TIPI; Gosling, Swann, Rentfrow, 2003).

We conducted two sets of analyses to test whether agreeable and conscientious individuals are indeed more likely to follow the advice of local leaders and experts. First, we tested whether Agreeableness and Conscientiousness predict higher self-reported levels of following the recommendations of community leaders (adherence-self). Second, we tested whether Agreeableness and Conscientiousness predict higher alignment between one's own behavior and the expected behavior of other community members (community-alignment), measured as the absolute difference between the adherence-self and adherence-other. To clearly demarcate our expected effects on community alignment from the potential effects of Agreeableness and Conscientiousness on perceiving oneself to be more compliant than others, we also calculated the signed difference between adherence-self and adherence-others (self-community-comparison); with scores bigger than zero indicating a participant's perception that they are more compliant than other community members, and scores lower than zero indicating the opposite). We ran linear regression analyses to regress the three outcomes - adherence self, community alignment, and community comparison - onto the Big Five personality traits in Model 1 and added the set of control variables in Model 2. The results are shown in the tables below (the reference categories for the categorical variables are "Male", "White", and "Full-time").


**Openness**

```{r, results='asis', echo = FALSE}
stargazer(m1, m2, m11, m12, m21, m22, type = "html", dep.var.labels = c("Adherence (Self)", "Community Alignment", "Community Comparison"), covariate.labels = c("Openness", "Age", "Gender (Female)", "Gender (Other)", "Education", "Ethnicity (Black)", "Ethnicity (Hispanic)", "Ethnicity (Asian)", "Ethnicity (Native American)", "Ethnicity (Middle Eastern)", "Ethnicity (Mixed)", "Ethnicity (Other)", "Employment (Part-time)", "Employment (Temporarily laid off)","Employment (Unemployed)","Employment (Retired)","Employment (Disabled)","Employment (Homemaker)","Employment (Student)","Employment (Other)","Political Ideology"))
```


**Conscientiousness**

```{r, results='asis', echo = FALSE}
stargazer(m3, m4, m13, m14, m23, m24, type = "html", dep.var.labels = c("Adherence (Self)", "Community Alignment", "Community Comparison"), covariate.labels = c("Conscientiousness", "Age", "Gender (Female)", "Gender (Other)", "Education", "Ethnicity (Black)", "Ethnicity (Hispanic)", "Ethnicity (Asian)", "Ethnicity (Native American)", "Ethnicity (Middle Eastern)", "Ethnicity (Mixed)", "Ethnicity (Other)", "Employment (Part-time)", "Employment (Temporarily laid off)","Employment (Unemployed)","Employment (Retired)","Employment (Disabled)","Employment (Homemaker)","Employment (Student)","Employment (Other)","Political Ideology"))
```


**Extraversion**

```{r, results='asis', echo = FALSE}
stargazer(m5, m6, m15, m16, m25, m26, type = "html", dep.var.labels = c("Adherence (Self)", "Community Alignment", "Community Comparison"), covariate.labels = c("Extraversion", "Age", "Gender (Female)", "Gender (Other)", "Education", "Ethnicity (Black)", "Ethnicity (Hispanic)", "Ethnicity (Asian)", "Ethnicity (Native American)", "Ethnicity (Middle Eastern)", "Ethnicity (Mixed)", "Ethnicity (Other)", "Employment (Part-time)", "Employment (Temporarily laid off)","Employment (Unemployed)","Employment (Retired)","Employment (Disabled)","Employment (Homemaker)","Employment (Student)","Employment (Other)","Political Ideology"))
```


**Agreeableness**

```{r, results='asis', echo = FALSE}
stargazer(m7, m8, m17, m18, m27, m28, type = "html", dep.var.labels = c("Adherence (Self)", "Community Alignment", "Community Comparison"), covariate.labels = c("Agreeableness", "Age", "Gender (Female)", "Gender (Other)", "Education", "Ethnicity (Black)", "Ethnicity (Hispanic)", "Ethnicity (Asian)", "Ethnicity (Native American)", "Ethnicity (Middle Eastern)", "Ethnicity (Mixed)", "Ethnicity (Other)", "Employment (Part-time)", "Employment (Temporarily laid off)","Employment (Unemployed)","Employment (Retired)","Employment (Disabled)","Employment (Homemaker)","Employment (Student)","Employment (Other)","Political Ideology"))
```


**Emotional Stability**

```{r, results='asis', echo = FALSE}
stargazer(m9, m10, m19, m20, m29, m30, type = "html", dep.var.labels = c("Adherence (Self)", "Community Alignment", "Community Comparison"), covariate.labels = c("Emotional Stability", "Age", "Gender (Female)", "Gender (Other)", "Education", "Ethnicity (Black)", "Ethnicity (Hispanic)", "Ethnicity (Asian)", "Ethnicity (Native American)", "Ethnicity (Middle Eastern)", "Ethnicity (Mixed)", "Ethnicity (Other)", "Employment (Part-time)", "Employment (Temporarily laid off)","Employment (Unemployed)","Employment (Retired)","Employment (Disabled)","Employment (Homemaker)","Employment (Student)","Employment (Other)","Political Ideology"))
```

In line with our expectations, we found that the extent to which a participant indicated to follow the recommendations of local community leaders and experts (adherence-self) was significantly related to both Agreeableness and Conscientiousness, but none of the other Big Five traits. In addition, we found that Agreeableness and Conscientiousness significantly predicted community alignment, suggesting that people scoring high on these traits are more likely to follow the norms of their local communities. The two other traits that significantly predicted community alignment were Extraversion and Emotional Stability. However, the follow up analyses for the community comparison outcome reveals that the effects for Extraversion and Emotional Stability are likely driven by the fact that neurotic individuals indicate that they are a lot more compliant than other community members and extraverts indicating that they are less. Agreeableness and Conscientiousness, in contrast, did not show any effects on the community comparison variable suggesting that they are about alignment rather than consistent over or under-compliance.


## Correlations Between Facebook Mobility Metrics and Google Mobility Metrics
```{r message=FALSE, warning=FALSE, echo = FALSE}
df_us_google <- read_csv("../Data/Google/2020_US_Region_Mobility_Report.csv")

fb_files <- list.files('../Data/FB Data/US individual files',
                       '*.csv', full.names = T)

df_us_socdist <- fb_files %>% 
  map(read_csv) %>% 
  bind_rows()

df_us_socdist <- df_us_socdist %>%
  select(-age_bracket, -gender, -baseline_name, 
         -baseline_type, -polygon_name) %>%
  rename(date = ds,
         county_fips = polygon_id,
         socdist_tiles = all_day_bing_tiles_visited_relative_change,
         socdist_single_tile = all_day_ratio_single_tile_users) %>%
  mutate(county_fips = as.character(county_fips))


df_us_fb <- df_us_socdist %>%
  select(county_fips, date, socdist_tiles, socdist_single_tile)

df_us_ggl <- df_us_google %>% 
  select(census_fips_code, date,
         retail_and_recreation_percent_change_from_baseline:residential_percent_change_from_baseline) %>%
  drop_na() %>%
  mutate(county_fips = as.character(as.numeric(census_fips_code))) %>%
  select(-census_fips_code)

df_us_fb_ggl <- df_us_fb %>% plyr::join(df_us_ggl, c('county_fips', 'date')) %>% drop_na()

df_us_fb_ggl %>% split(.$county_fips) %>%
  map(~ map_if(., is.numeric, scale)) %>%
  bind_rows() %>%
  select(socdist_tiles:residential_percent_change_from_baseline) %>%
  drop_na() %>%
  cor() %>% 
  as.data.frame() %>%
  select(c(1,2)) %>% round(3) %>% datatable()
```
Note: Pearson correlations of Facebook and Google mobility metrics (28) in the US. Values were standardized within regions in order to control for baseline differences. The Facebook mobility metrics are based on 1) the number of Bing tiles visited by the individuals in each region and 
2) the proportion of individuals within each region who stay within a single tile, relative to a pre-COVID baseline. The Google metrics are based on the number of visits by individuals within a region to the six different place categories, relative to a pre-COVID baseline.


## Assessment of Covid-19 Onset Threshold Values
```{r, warning=FALSE, message=FALSE, echo=FALSE}
df_us_prev <- read_csv('../Data/US/US_prevalence.csv')

df_us_prev <- df_us_prev %>% 
  select(fips, date, rate) %>% 
  mutate(date = as.Date(date, "%d%b%Y")) %>% 
  dplyr::rename(county_fips = fips, 
         rate_day = rate) %>%
  mutate(county_fips = as.character(county_fips)) %>% 
  filter(rate_day >= 0 & rate_day <= 1000) %>%
  filter(date <= '2020-04-15')
  

# create sequence of dates
date_sequence <- seq.Date(min(df_us_prev$date),
                          max(df_us_prev$date), 1)
                     
# create data frame with time sequence
df_dates = data.frame(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# join data frames
df_us_prev <- df_us_prev %>%
  merge(df_dates, by='date') %>% 
  arrange(county_fips, date) %>% 
  drop_na()


onset_times <- c()
censored <- c()

thresh <- seq(0.01, 1, 0.01)

for (i in thresh){

# get onset day
df_us_onset_prev <- df_us_prev %>% 
  group_by(county_fips) %>%
  filter(rate_day > i) %>%
  summarise(onset_prev = min(time))

# merge with county data
df_us_onset_prev <- df_us_prev %>%
  select(-date, -time, -rate_day) %>%
  distinct() %>%
  mutate(county_fips = as.character(county_fips)) %>%
  left_join(df_us_onset_prev, by = 'county_fips')

# handle censored data
df_us_onset_prev <- df_us_onset_prev %>%
  mutate(event = ifelse(is.na(onset_prev), 0, 1)) %>%
  mutate(onset_prev = replace_na(onset_prev, as.numeric(diff(range(df_us_prev$date)))+1)) %>%
  mutate(onset_prev = onset_prev-min(onset_prev))

  onset_times <- c(onset_times, df_us_onset_prev$onset_prev %>% mean())
  censored <- c(censored, df_us_onset_prev$event %>% mean())

}

#plot(thresh, onset_times)
plot(thresh, 1-censored, xlab="Cases/1000 inhabitants", 
     ylab="Proportion of censored counties", main="Proportion of censored units and onset threshold (US)")


df_ger_prev <- read_csv('../Data/GER/GER_prevalence.csv')

df_ger_prev <- df_ger_prev %>%
  mutate(date = as.Date(date, "%d%b%Y"),
         kreis = as.character(kreis)) %>% 
  dplyr::select(kreis, date, rate_day) %>%
  filter(date < '2020-04-01')
  

# create sequence of dates
date_sequence <- seq.Date(min(df_ger_prev$date),
                          max(df_ger_prev$date), 1)
                     
# create data frame with time sequence
df_dates = data.frame(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# join data frames
df_ger_prev <- df_ger_prev %>%
  merge(df_dates, by='date') %>% 
  arrange(kreis, date) %>% 
  drop_na()


onset_times <- c()
censored <- c()

thresh <- seq(0.01, 1, 0.01)

for (i in thresh){

# get onset day
df_ger_onset_prev <- df_ger_prev %>% 
  group_by(kreis) %>%
  filter(rate_day > i) %>%
  summarise(onset_prev = min(time))

# merge with county data
df_ger_onset_prev <- df_ger_prev %>%
  select(-date, -time, -rate_day) %>%
  distinct() %>%
  mutate(kreis = as.character(kreis)) %>%
  left_join(df_ger_onset_prev, by = 'kreis')

# handle censored data
df_ger_onset_prev <- df_ger_onset_prev %>%
  mutate(event = ifelse(is.na(onset_prev), 0, 1)) %>%
  mutate(onset_prev = replace_na(onset_prev, as.numeric(diff(range(df_ger_prev$date)))+1)) %>%
  mutate(onset_prev = onset_prev-min(onset_prev))

  onset_times <- c(onset_times, df_ger_onset_prev$onset_prev %>% mean())
  censored <- c(censored, df_ger_onset_prev$event %>% mean())

}

#plot(thresh, onset_times)
plot(thresh, 1-censored, xlab="Cases/1000 inhabitants", 
     ylab="Proportion of censored counties", main="Proportion of censored units and onset threshold (GER)")
```

Note. Proportion of censored units (geographic units with no onset) are shown as a function of onset threshold values between 1/100000 and 1/1000. The threshold of 1/1000 was chosen based on the distribution of the observed data. Choosing a very low threshold would have made the onset dates noisy, choosing a very high threshold would have resulted in many geographic units with no onset in the chosen time frame. The threshold of 1/10000 was chosen, because it is not overly sensitive to noise while also minimizing the proportion of censored units (0 in Germany, 0.3 in the US).



**References:**

1. AL-Omiri, M. K. et al. COVID-19 and personality: a cross-sectional multicenter study of the relationship between personality factors and COVID-19-related impacts, concerns, and behaviors. Front Psychiatry. 12, 608730 (2021).
2.	Aschwanden, D. et al. Psychological and behavioural responses to Coronavirus disease 2019: the role of personality. Eur J Pers. 35, 51-66 (2021).
3.	Bogg, T. & Milad, E. Demographic, personality, and social cognition correlates of Coronavirus guideline adherence in a U.S. sample. Health Psychol. 39, 1026-1036 (2020).
4.	Han, H. Exploring the association between compliance with measures to prevent the spread of COVID-19 and big five traits with Bayesian generalized linear model. Pers Individ Dif. 176, 110787 (2021).
5.	Ludeke, S. G., Vitriol, J. A., Larsen, E. G. & Gensowski, M. Personality in a pandemic: social norms moderate associations between personality and social distancing behaviors. Pers Individ Dif. 177, 110828 (2021).
6.	Chan, H. F. et al. Can psychological traits explain mobility behavior during the COVID-19 pandemic? Soc Psychol Personal Sci. 12, 1018-1029 (2020).
7.	Götz, F. M., Andrés, G., Galinsky, A. D. & Jachimowicz, J. M. How personality and policy predict pandemic behavior: understanding sheltering-in-place in 55 countries at the onset of COVID-19. Am Psychol. 76, 39-49 (2021).
8.	Airaksinen, J., Komulainen, K., Jokela, M. & Gluschkoff, K. Big five personality traits and COVID-19 precautionary behaviors among older adults in Europe. Preprint at https://psyarxiv.com/rvbjf (2021).
9.	Clark, C., Davila, A., Regis, M. & Kraus, S. Predictors of COVID-19 voluntary compliance behaviors: an international investigation. Glob Transit. 2, 76-82 (2020).
10.	Nofal, A. M., Cacciotti, G. & Lee, N. Who complies with COVID-19 transmission mitigation behavioral guidelines? PLoS One. 15, e0240396 (2020).
11.	Qian, K. & Yahara, T. Mentality and behavior in COVID-19 emergency status in Japan: influence of personality, morality and ideology. PLoS One. 15, e0235883 (2020).
12.	Rammstedt, B., Lechner, C. M. & Weiß, B. Does personality predict responses to the COVID-19 crisis? Evidence from a prospective large-scale study. Eur J Pers. OnlineFirst at https://doi.org/10.1177/0890207021996970 (2021).
13.	Wright, L. & Fancourt, D. Do predictors of adherence to pandemic guidelines change over time? A panel study of 21,000 UK adults during the COVID-19 pandemic. Preprint at https://doi.org/10.1101/2020.11.10.20228403 (2020).
14.	Zettler, I. et al. The role of personality in COVID-19-related perceptions, evaluations, and behaviors: findings across five samples, nine traits, and 17 criteria. Soc Psychol Personal Sci. OnlineFirst at https://doi.org/10.1177%2F19485506211001680 (2021).
15.	Abdelrahman, M. Personality traits, risk perception, and protective behaviors of Arab residents of Qatar during the COVID-19 pandemic. Int J Ment Health Addict. 22, 1-12 (2020).
16.	Blagov, P. S. Adaptive and dark personality in the COVID-19 pandemic: predicting health-behavior endorsement and the appeal of public-health messages. Soc Psychol Personal Sci. 12, 697-707 (2021).
17.	Carvalho, L. F., Pianowski, G. & Gonçalves, A. P. Personality differences and COVID-19: are extroversion and conscientiousness personality traits associated with engagement with containment measures? Trends Psychiatry Psychother. 42, 179-184 (2020).
18.	Brouard, S., Vasilopoulos, P. & Becher, M. Sociodemographic and psychological correlates of compliance with the COVID-19 public health measures in France. Can J Polit Sci. 1-6 (2020).
19.	Krupić, Di., Žuro, B. & Krupić, Da. Big five traits, approach-avoidance motivation, concerns and adherence with COVID-19 prevention guidelines during the peak of pandemic in Croatia. Pers Individ Dif. 179, 110913 (2021).
20.	Shook, N. J., Sevi, B., Lee, J., Oosterhoff, B. & Fitzgerald, H. N. Disease avoidance in the time of COVID-19: the behavioral immune system is associated with concern and preventative health behaviors. PLoS One. 15, e0238015 (2020).
21.	Asselmann, E., Borghans, L., Montizaan, R. & Seegers, P. The role of personality in the thoughts, feelings, and behaviors of students in Germany during the first weeks of the COVID-19 pandemic. PLoS One. 15, e0242904 (2020).
22.	Zajenkowski, M., Jonason, P. K., Leniarska, M. & Kozakiewicz, Z. Who complies with the restrictions to reduce the spread of COVID-19? Personality and perceptions of the COVID-19 situation. Pers Individ Dif. 166, 110199 (2020).
23. United States Census Bureau, United States Census Bureau Databases, https://www.census.gov (June 26, 2020).
24. Institut für Bau, Stadt- und Raumforschung, Indikatoren und Karten zur Raum- und Stadtentwicklung https://www.inkar.de (June 26, 2020).
25. National Centers for Environmental Information 2021. GHCN Daily dataset. doi: https://www.ncei.noaa.gov/pub/data/
26. Deutscher Wetterdienst 2021. Climate Data Center. doi: https://cdc.dwd.de/portal/
27. Gosling, S. D., Rentfrow, P. J., & Swann Jr, W. B. (2003). A very brief measure of the Big-Five personality domains. Journal of Research in personality, 37(6), 504-528.
28. Google, Google Mobility Reports, https://www.google.com/covid19/mobility/ (October 25, 2020)

