---
title: "COVID-19 US"
author: "Heinrich Peters"
date: "11/04/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# MAC
 knitr::opts_knit$set(root.dir = '/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Data/US')

library(Hmisc)
library(lmerTest)
library(nlme)
library(psych)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(party)
library(doParallel)
library(changepoint)
library(survival)
library(survminer)
library(censReg)
 
source('/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Code/COVID19_functions.R')
```

# Prepare county level data 
### Read and format prevalence data 
```{r, warning=FALSE, message=FALSE}
df_us_prev <- read_csv('US_prevalence.csv')

df_us_prev <- df_us_prev %>% 
  select(fips, date, rate) %>% 
  mutate(date = as.Date(date, "%d%b%Y")) %>% 
  rename(county_fips = fips, 
         rate_day = rate) %>%
  mutate(county_fips = as.character(county_fips)) %>% 
  filter(rate_day >= 0 & rate_day <= 1000) %>%
  filter(date <= '2020-05-15')
```

```{r}
df_us_death <- read_csv('US_prevalence.csv')

df_us_death <-df_us_death %>%
  mutate(date = as.Date(date, "%d%b%Y"), 
         fips = as.character(fips))

df_us_death <- df_us_death %>% 
  filter(date == '2020-09-30') %>% 
  rename(county_fips = fips,
         case_rate = rate,
         death_rate = rate_death) %>% 
  select(county_fips, case_rate, death_rate)
```

### Read and format personality data 
```{r, warning=FALSE, message=FALSE}
df_us_pers <- read_csv('US_personality_2.csv')

df_us_pers <- df_us_pers %>%
  dplyr::rename(county_fips = county,
         pers_o = open, 
         pers_c = sci,
         pers_e = extra,
         pers_a = agree,
         pers_n = neuro) %>%
  filter(freq >= 50) %>%
  select(-county_name, -freq) %>%
  mutate(county_fips = as.character(county_fips))
```

### Read and format county level controls 
```{r}
df_us_ctrl <- read.csv('US_controls_2.csv')

df_us_ctrl <- df_us_ctrl %>% select(-county_name) %>%
  rename(county_fips = county,
         airport_dist = airport_distance,
         conservative = republican,
         age = medage,
         healthcare = physician_pc) %>%
  mutate(county_fips = as.character(county_fips))
```

### Read and format social distancing data FB
```{r, warning=FALSE, message=FALSE}
fb_files <- list.files('../FB Data/US individual files',
                       '*.csv', full.names = T)

df_us_socdist <- fb_files %>% 
  map(read_csv) %>% bind_rows()

df_us_socdist <- df_us_socdist %>%
  select(-age_bracket, -gender, -baseline_name, -baseline_type, -polygon_name) %>%
  rename(date = ds,
         county_fips = polygon_id,
         socdist_tiles = all_day_bing_tiles_visited_relative_change,
         socdist_single_tile = all_day_ratio_single_tile_users) %>%
  mutate(county_fips = as.character(county_fips))
```

### Merge prevalence data
```{r}
# create sequence of dates
date_sequence <- seq.Date(min(df_us_prev$date),
                          max(df_us_prev$date), 1)
                     
# create data frame with time sequence
df_dates = data.frame(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# join data frames 
df_us_prev <- df_us_prev %>%
  plyr::join(df_us_ctrl, by='county_fips') %>% 
  plyr::join(df_us_pers, by='county_fips') %>%
  merge(df_dates, by='date') %>% 
  arrange(county_fips, date)
```

```{r}
# join data frames 
df_us_death <- df_us_death %>%
  plyr::join(df_us_ctrl, by='county_fips') %>% 
  plyr::join(df_us_pers, by='county_fips')
```

### Merge social distancing data
```{r}
# create sequence of dates
date_sequence <- seq.Date(min(df_us_socdist$date),
                          as.Date('2020-04-28'), 1)
                     
# create data frame with time sequence
df_dates = data.frame(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# join data frames 
df_us_socdist <- df_us_socdist %>%
  plyr::join(df_us_ctrl, by='county_fips') %>% 
  plyr::join(df_us_pers, by='county_fips') %>%
  inner_join(df_dates, by='date') %>% 
  arrange(county_fips, date)

fips_complete <- df_us_socdist %>% 
  group_by(county_fips) %>% 
  summarise(n = n()) %>% 
  filter(! n<max(n)) %>% .$county_fips

df_us_socdist <- df_us_socdist %>%
  filter(county_fips %in% fips_complete)
```

### Control for weekend effect 
```{r}
easter <- seq.Date(as.Date('2020-04-10'), as.Date('2020-04-13'), 1)

df_us_loess <- df_us_socdist %>% 
  mutate(weekday = format(date, '%u')) %>% 
  filter(!weekday %in% c('6','7') | date %in% easter) %>% 
  split(.$county_fips) %>%
  map(~ loess(socdist_single_tile ~ time, data = .)) %>%
  map(predict, 1:max(df_us_socdist$time)) %>% 
  bind_rows() %>% 
  gather(key = 'county_fips', value = 'loess') %>% 
  group_by(county_fips) %>% 
  mutate(time = row_number())

df_us_loess_2 <- df_us_socdist %>% 
  mutate(weekday = format(date, '%u')) %>% 
  filter(!weekday %in% c('6','7') | date %in% easter) %>% 
  split(.$county_fips) %>%
  map(~ loess(socdist_tiles ~ time, data = .)) %>%
  map(predict, 1:max(df_us_socdist$time)) %>% 
  bind_rows() %>% 
  gather(key = 'county_fips', value = 'loess') %>% 
  rename(loess_2 = loess) %>%
  group_by(county_fips) %>% 
  mutate(time = row_number())

df_us_socdist <- df_us_socdist %>% 
  merge(df_us_loess, by=c('county_fips', 'time')) %>% 
  merge(df_us_loess_2, by=c('county_fips', 'time')) %>% 
  mutate(weekday = format(date, '%u')) %>% 
  mutate(socdist_single_tile_clean = ifelse(weekday %in% c('6','7') | date %in% easter, 
                                            loess, socdist_single_tile),
         socdist_tiles_clean = ifelse(weekday %in% c('6','7') | date %in% easter, 
                                            loess_2, socdist_tiles)) %>%
  arrange(county_fips, time) %>% 
  select(-weekday)

df_us_socdist <- df_us_socdist %>% drop_na() %>% mutate(time = time-1)
```

### Pick cleaned social distancing metrics
```{r}
df_us_socdist <- df_us_socdist %>% 
  mutate(socdist_single_tile = socdist_single_tile_clean,
         socdist_tiles = socdist_tiles_clean) %>% 
  select(-loess, -loess_2, -socdist_single_tile_clean, -socdist_tiles_clean)
```

### Rescale Data
```{r}
lvl2_scaled <- df_us_prev %>% 
  select(-time, -date, -rate_day) %>% 
  distinct() %>% 
  mutate_at(vars(-county_fips), scale)

lvl1_scaled <- df_us_prev %>% select(county_fips, date, time, rate_day)

df_us_prev_scaled <- plyr::join(lvl1_scaled, lvl2_scaled, by = 'county_fips') 
```

```{r}
df_us_death_scaled <- df_us_death %>% 
  mutate_at(vars(-county_fips), scale)
```

```{r}
lvl2_scaled <- df_us_socdist %>%
  select(-time, -date, -socdist_tiles, -socdist_single_tile) %>% 
  distinct() %>% 
  mutate_at(vars(-county_fips), scale)

lvl1_scaled <- df_us_socdist %>% 
  select(county_fips, date, time, socdist_single_tile, socdist_tiles)

df_us_socdist_scaled <- plyr::join(lvl1_scaled, lvl2_scaled, by = 'county_fips') 
```

# Define outcomes of interest
### COVID - Extract onset
```{r}
# get onset day
df_us_onset_prev <- df_us_prev_scaled %>% 
  filter(date <= '2020-04-15') %>%
  group_by(county_fips) %>% 
  filter(rate_day > 0.1) %>%
  summarise(onset_prev = min(time))

# merge with county data
df_us_onset_prev <- df_us_prev_scaled %>%
  select(-date, -time, -rate_day) %>%
  distinct() %>%
  mutate(county_fips = as.character(county_fips)) %>%
  left_join(df_us_onset_prev, by = 'county_fips')

# handle censored data
df_us_onset_prev <- df_us_onset_prev %>%
  mutate(event = ifelse(is.na(onset_prev), 0, 1)) %>%
  mutate(onset_prev = replace_na(onset_prev, as.numeric(diff(range(df_us_prev$date)))+1))
```

### COVID - Extract slopes
```{r}
# cut time series before onset
df_us_prev_scaled <- df_us_prev_scaled %>%
  filter(date <= '2020-05-15') %>%
  group_by(county_fips) %>%
  filter(rate_day > 0.1) %>%
  mutate(time = time-min(time)+1) %>%
  ungroup() %>%
  filter(time <= 30)

# extract slope prevalence
df_us_slope_prev <- df_us_prev_scaled %>% 
  split(.$county_fips) %>% 
  map(~ lm(log(rate_day+1) ~ time, data = .)) %>%
  map(coef) %>% 
  map_dbl('time') %>% 
  as.data.frame() %>% 
  rownames_to_column('county_fips') %>% 
  rename(slope_prev = '.')
  
# merge with county data
df_us_slope_prev <- df_us_onset_prev %>% 
  left_join(df_us_slope_prev, by = 'county_fips') %>%
  mutate(slope_prev = replace_na(slope_prev, 0))

# standardize slopes
df_us_slope_prev <- df_us_slope_prev %>%
  mutate(slope_prev = scale(slope_prev),
         onset_prev = scale(onset_prev))
```


### Social Distancing - Change point analysis
```{r}
# keep only counties with full data
fips_complete <- df_us_socdist_scaled %>% 
  group_by(county_fips) %>% 
  summarise(n = n()) %>% 
  filter(n==max(.$n)) %>% 
  .$county_fips

# run changepoint analysis
df_us_socdist_cpt_results <- df_us_socdist_scaled %>% 
  select(county_fips, socdist_single_tile) %>%
  filter(county_fips %in% fips_complete) %>% 
  split(.$county_fips) %>%
  map(~ cpt.meanvar(as.vector(.$socdist_single_tile),
                    #penalty = 'Asymptotic',
                    class=TRUE,
                    param.estimates=TRUE,
                    Q=1,
                    test.stat = 'Normal'))

df_us_socdist_cpt_results_2 <- df_us_socdist_scaled %>% 
  select(county_fips, socdist_tiles) %>%
  filter(county_fips %in% fips_complete) %>% 
  split(.$county_fips) %>%
  map(~ cpt.meanvar(as.vector(.$socdist_tiles),
                    #penalty = 'Asymptotic',
                    class=TRUE,
                    param.estimates=TRUE,
                    Q=1,
                    test.stat = 'Normal'))

# calculate change point
df_us_socdist_cpt_day <- df_us_socdist_cpt_results %>% 
  map(cpts) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cpt_day_socdist = '.') %>%
  rownames_to_column('county_fips')

df_us_socdist_cpt_day_2 <- df_us_socdist_cpt_results_2 %>% 
  map(cpts) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cpt_day_socdist_2 = '.') %>%
  rownames_to_column('county_fips')

# calculate mean differences
df_us_socdist_cpt_mean_diff <- df_us_socdist_cpt_results %>% 
  map(param.est) %>% 
  map(~ .$mean) %>% 
  map(~ .[2]) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mean_diff_socdist = '.') %>%
  rownames_to_column('county_fips')

df_us_socdist_cpt_mean_diff_2 <- df_us_socdist_cpt_results_2 %>% 
  map(param.est) %>% 
  map(~ .$mean) %>% 
  map(~ -.[2]) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mean_diff_socdist_2 = '.') %>%
  rownames_to_column('county_fips')

# calculate means
df_us_socdist_mean <- df_us_socdist_scaled %>%
  group_by(county_fips) %>%
  summarise(mean_socdist = mean(socdist_single_tile))

df_us_socdist_mean_2 <- df_us_socdist_scaled %>%
  group_by(county_fips) %>%
  summarise(mean_socdist_2 = -mean(socdist_tiles))

# merge with county data
df_us_cpt_socdist <- df_us_socdist_scaled %>% 
  select(-time, -date, -socdist_single_tile, -socdist_tiles) %>%
  distinct() %>% 
  left_join(df_us_socdist_cpt_day, by='county_fips') %>%
  left_join(df_us_socdist_cpt_day_2, by='county_fips') %>%
  left_join(df_us_socdist_cpt_mean_diff, by='county_fips') %>%
  left_join(df_us_socdist_cpt_mean_diff_2, by='county_fips') %>%
  left_join(df_us_socdist_mean, by='county_fips') %>%
  left_join(df_us_socdist_mean_2, by='county_fips') %>%
  left_join(select(df_us_onset_prev, county_fips, onset_prev), by='county_fips') %>%
  left_join(select(df_us_slope_prev, county_fips, slope_prev), by='county_fips') 

# standardize mean/var differences
df_us_cpt_socdist <- df_us_cpt_socdist %>% 
  mutate(mean_diff_socdist = scale(mean_diff_socdist),
         mean_diff_socdist_2 = scale(mean_diff_socdist_2),
         mean_socdist = scale(mean_socdist),
         mean_socdist_2 = scale(mean_socdist_2))

# handle censored data
df_us_cpt_socdist <- df_us_cpt_socdist %>% 
  mutate(cpt_day_socdist = ifelse(is.na(cpt_day_socdist), as.numeric(diff(range(df_us_socdist$date))), cpt_day_socdist)) %>% 
  mutate(event = ifelse(cpt_day_socdist >= as.numeric(diff(range(df_us_socdist$date))), 0, 1))
```


# Fit models
### Predict COVID onset
```{r}
us_cox_prev_onset <- run_analyses(y = 'onset_prev',  data = df_us_slope_prev, model = 'cox')
```

### Predict COVID growth
```{r}
us_lm_prev_slope <- run_analyses(y = 'slope_prev',  data = df_us_slope_prev, model = 'lm')
```

### Predict COVID case rate
```{r}
us_lm_prev_cases <- run_analyses(y = 'case_rate',  data = df_us_death_scaled, model = 'lm')
```

### Predict COVID death rate
```{r}
us_lm_prev_deaths <- run_analyses(y = 'death_rate',  data = df_us_death_scaled, model = 'lm')
```

### Predict socdist change points
```{r}
us_cox_socdist_cpt <- run_analyses(y = 'cpt_day_socdist_2',  data = df_us_cpt_socdist, model = 'cox')
```

### Predict socdist means
```{r}
us_lm_socdist_mean <- run_analyses(y = 'mean_diff_socdist_2',  data = df_us_cpt_socdist, model = 'lm')
```

# Export data 
```{r}
us_list_results <- list(us_cox_prev_onset, us_lm_prev_slope,
                        us_lm_prev_cases, us_lm_prev_deaths,
                         us_cox_socdist_cpt, us_lm_socdist_mean)

us_results_names <- list('us_cox_prev_onset', 'us_lm_prev_slope',
                         'us_lm_prev_cases', 'us_lm_prev_deaths',
                      'us_cox_socdist_cpt', 'us_lm_socdist_mean')

names(us_list_results) <- us_results_names

save(us_list_results, file="us_list_results_robustness_check.RData")
```

# Extract results
### Results - predict COVID onset
```{r}
us_agg_prev_onset <- us_list_results$us_cox_prev_onset %>% extract_all()
```

### Results - predict COVID growth
```{r}
us_agg_prev_slope <- us_list_results$us_lm_prev_slope %>% extract_all()
```

### Results - predict COVID case rates
```{r}
us_agg_prev_cases <- us_list_results$us_lm_prev_cases %>% extract_all()
```

### Results - predict COVID death rates
```{r}
us_agg_prev_deaths <- us_list_results$us_lm_prev_deaths %>% extract_all()
```

### Results - predict socdist start
```{r}
us_agg_socdist_cpt <- us_list_results$us_cox_socdist_cpt %>% extract_all()
```

### Results - predict socdist means
```{r}
us_agg_socdist_mean <- us_list_results$us_lm_socdist_mean %>% extract_all()
```

### Save aggregated results
```{r}
us_agg_fixed_window <- list(us_agg_prev_onset,
               us_agg_prev_slope,
               us_agg_prev_cases,
               us_agg_prev_deaths,
               us_agg_socdist_cpt,
               us_agg_socdist_mean
               )

names(us_agg_fixed_window) <- us_results_names

save(us_agg_fixed_window, file="us_agg_robustness_ckeck.RData")
```

```{r}
write_csv(df_us_slope_prev, 'df_us_slope_prev_robustness_check.csv')
write_csv(df_us_cpt_socdist, 'df_us_cpt_socdist_robustness_check.csv')
```

### Display aggregated results 
```{r}
us_agg_fixed_window
```

