---
title: "COVID-19 US Counties"
author: "Heinrich Peters"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# MAC
 knitr::opts_knit$set(root.dir = '/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Data')
 
 library(tidyverse)
 library(lmerTest)
 library(nlme)
 library(psych)
 library(ggplot2)
```


# Prepare county level data 

### Read and format data
```{r, warning=FALSE, message=FALSE}

df_us_covid <- read_csv('timeseries_usa_county_march1_april_09.csv')
df_us_covid <- df_us_covid %>% 
  filter(time <=31) %>% 
  arrange(countyfips) %>%
  mutate(stabil = -stabil) %>%
  rename(county_fips = countyfips,
         pers_o = open, 
         pers_c = sci,
         pers_e = extra,
         pers_a = agree,
         pers_n = stabil)

df_us_covid %>% head()

df_us_socdisc <- read_csv('0409_sds-full-county.csv')

df_us_socdisc %>% head()


```

### Format time variable
```{r}

# create sequence of dates
date_sequence <- seq.Date(as.Date('2020-03-01'),
                          as.Date('2020-03-31'), 1)
date_sequence
                     

# create data frame with time sequence
df_dates = tibble(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# merge day index with gps data
df_us_socdisc = df_us_socdisc %>% 
  merge(df_dates, by='date') %>% 
  arrange(county_fips) %>%
  as_tibble()

```

## Merge data
```{r}
df_us <- plyr::join_all(list(df_us_covid, df_us_socdisc), 
                  by = c('county_fips', 'time'), 
                  type = 'inner') %>% 
  arrange(county_fips, time)

df_us %>% head()

```

## Explore data
### Plot distributions
```{r}

# distribution of observations per county
df_us %>% group_by(county_fips) %>% 
  summarise(mark = mean(mark)) %>% 
  ggplot(aes(x=mark)) + 
  geom_histogram(color="black", fill="white", binwidth = 300) +
  ggtitle('Distribution of observations per county')

  
# distributions of mean corona rates per county
df_us %>% group_by(county_fips) %>% 
  summarise(rate_day = mean(rate_day)) %>%
  ggplot(aes(x=rate_day)) + 
  geom_histogram(color="black", fill="white", binwidth = 0.01) +
  ggtitle('Distribution of mean corona rates by county')

  
# distribution of mean sd distance measue
df_us %>% group_by(county_fips) %>% 
  summarise(daily_distance_diff = mean(daily_distance_diff)) %>%
  ggplot(aes(x=daily_distance_diff)) + 
  geom_histogram(color="black", fill="white") +
 ggtitle('Distribution of mean sd distance measure by county')


# distribution of mean sd visit measue
df_us %>% group_by(county_fips) %>% 
  summarise(daily_visitation_diff = mean(daily_visitation_diff)) %>%
  ggplot(aes(x=daily_visitation_diff)) + 
  geom_histogram(color="black", fill="white") +
  ggtitle('Distribution of mean sd visit measure by county')


```


```{r}

df_us %>% group_by(county_fips) %>% 
  slice(n()) %>% 
  group_by(state) %>% 
  summarise(county_n = n()) %>% 
  ggplot(aes(x=state, y=county_n)) +
  geom_bar(stat="identity") + 
  ggtitle('Counties per state') +
  coord_flip()


df_us %>% 
  group_by(state) %>% 
  summarise(individual_n = sum(mark)) %>% 
  ggplot(aes(x=state, y=individual_n)) +
  geom_bar(stat="identity") +
  ggtitle('Individuals per state') +
  coord_flip()  


```

### Plot social distancing by distance travelled
```{r}

df_us %>% sample_n(5000) %>%
  ggplot(aes(x=time, y=daily_distance_diff)) + 
  geom_point(aes(col=county_name, size=mark)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall social distancing (distance travelled) over time")


pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

gg <- df_us %>% mutate(dist_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.01), quantile(.[[i]], 0.99), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(dist_tail != 'center') %>%
  ggplot(aes(x=time, y=daily_distance_diff)) + 
  geom_point(aes(col=county_name, size=mark)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~dist_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```
### Plot social distancing by place visits
```{r}

df_us %>% sample_n(5000) %>%
  ggplot(aes(x=time, y=daily_visitation_diff)) + 
  geom_point(aes(col=county_name, size=mark)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall social distancing (places visited) over time")



pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

gg <- df_us %>% mutate(dist_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.01), quantile(.[[i]], 0.99), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(dist_tail != 'center') %>%
  ggplot(aes(x=time, y=daily_visitation_diff)) + 
  geom_point(aes(col=county_name, size=mark)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~dist_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```


### Plot prevalence over time
```{r}

df_us %>% sample_n(5000) %>%
  ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=county_name, size=mark)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall prevalence over time")



pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

  
gg <- df_us %>% mutate(dist_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.01), quantile(.[[i]], 0.99), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(dist_tail != 'center') %>%
  ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=county_name, size=mark)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~dist_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```


### Correlations 

```{r}

df_us %>% select(county_fips, population, acad_share, medianage, 
                 creative_share, rep2012, male_share, medianinc, 
                 lifeexp_2010_14, black_share, foreign_share, 
                 married_share, patents, popdens, viocrime, 
                 pers_o, pers_a, pers_e, pers_c, pers_n, mark, 
                 rate_day, daily_distance_diff, daily_visitation_diff, 
                 encounters_rate) %>% 
  group_by(county_fips) %>%
  summarize_if(is.numeric, mean) %>% 
  cor(use='pairwise.complete.obs')
  
```



## Rescale Data
```{r}
df_us <- df_us %>% select(county_fips, date, time, pers_o, pers_c, pers_e, pers_e, pers_a, pers_n,
                 daily_distance_diff, rate_day) %>%
  mutate_at(vars(-county_fips, -date, -time), scale)

df_us %>% head()
```


# Model building

## Prepare functions

```{r}

# function calculates all relevant models
run_models <- function(y, lvl1_x, lvl2_x, lvl2_id, data){

  # subset data
  data = data %>% 
    dplyr::select(all_of(y), all_of(lvl1_x), all_of(lvl2_x), all_of(lvl2_id))
  data = data %>% 
    rename(y = all_of(y),
           lvl1_x = all_of(lvl1_x),
           lvl2_x = all_of(lvl2_x),
           lvl2_id = all_of(lvl2_id)
           )
  
  # configure optimization procedure
  ctrl_config <- lmeControl(opt = 'optim')

  # baseline
  baseline <- lme(fixed = y ~ 1, random = ~ 1 | lvl2_id, 
                    data = data,
                    correlation = corAR1(),
                  control = ctrl_config)

  # random intercept fixed slope
  random_intercept <- lme(fixed = y ~ lvl1_x + lvl2_x , random = ~ 1 | lvl2_id,
                            data = data,
                            correlation = corAR1(),
                  control = ctrl_config)

  # random intercept random slope
  random_slope <- lme(fixed = y ~ lvl1_x + lvl2_x, random = ~ lvl1_x | lvl2_id, 
                        data = data,
                        correlation = corAR1(),
                  control = ctrl_config)

  # cross level interaction
  interaction <- lme(fixed = y ~ lvl1_x * lvl2_x, random = ~ lvl1_x | lvl2_id, 
                       data = data,
                       correlation = corAR1(),
                  control = ctrl_config)
  
  # create list with results
  results <- list('baseline' = baseline, 
                  "random_intercept" = random_intercept, 
                  "random_slope" = random_slope,
                  "interaction" = interaction)
  
  return(results)
        
}


# extracts table with coefficients and tests statistics
extract_results <- function(models) {
  
  models_summary <- models %>% 
  map(summary) %>% 
  map("tTable") %>% 
  map(as.data.frame) %>% 
  map(round, 5) %>% 
  map(~ .[str_detect(rownames(.), 'Inter|lvl'),])
  
  return(models_summary)
}
```


## Predict prevalence
### prevalence ~ openness
```{r}

models_o_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_o', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_o_covid)

```

### prevalence ~ conscientiousness
```{r}

models_c_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_c', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_c_covid)

```

### prevalence ~ extraversion
```{r}

models_e_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_e', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_e_covid)

```

### prevalence ~ agreeableness
```{r}

models_a_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_a', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_a_covid)

```

### prevalence ~ neuroticism
```{r}

models_n_covid <-run_models(y = 'rate_day', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_n', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_n_covid)

```



## Predict social distancing
### social distancing ~ openness
```{r}

models_o_sd <-run_models(y = 'daily_distance_diff', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_o', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_o_sd)

```

### social distancing ~ conscientiousness
```{r}

models_c_sd <-run_models(y = 'daily_distance_diff', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_c', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_c_sd)

```

### social distancing ~ extraversion
```{r}

models_e_sd <-run_models(y = 'daily_distance_diff', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_e', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_e_sd)

```

### social distancing ~ agreeableness
```{r}

models_a_sd <-run_models(y = 'daily_distance_diff', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_a', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_a_sd)

```

### social distancing ~ neuroticism
```{r}

models_n_sd <-run_models(y = 'daily_distance_diff', 
                         lvl1_x = 'time', 
                         lvl2_x = 'pers_n', 
                         lvl2_id = 'county_fips', 
                         data = df_us)

extract_results(models_n_sd)

```
