---
title: "COVID19 UK"
author: "Heinrich Peters"
date: "4/23/2020"
output: html_notebook
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# MAC
 knitr::opts_knit$set(root.dir = '/Users/hp2500/Google Drive/STUDY/Columbia/Research/Corona/Data/UK')
 
library(lmerTest)
library(nlme)
library(psych)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(party)
library(doParallel)
library(changepoint)
library(survival)
library(survminer)

```

# Prepare data

### Read and format data

### Prevalence 

```{r}
df_uk_prev <- read_csv('UK_timeseries_prep_2005.csv')

df_uk_prev <- df_uk_prev %>% 
  select(ut_area, date, rate) %>% 
  rename(rate_day = rate) %>%
  mutate(date = as.Date(date, "%d%b%Y"))

df_uk_prev
```

### Personality
```{r}

df_uk_pers <- read_csv('timeseries_uk_utla_march9_april_09.csv')

df_uk_pers <- df_uk_pers %>% 
  select(ut_area, open, agree, neuro, sci, extra) %>% 
  dplyr::rename(pers_o = open, 
         pers_c = sci,
         pers_e = extra,
         pers_a = agree,
         pers_n = neuro) %>%
  distinct()

df_uk_pers

```

### Social distancing
```{r}
df_uk_socdist <- read_csv('UK_socdist_fb_nuts3.csv')
df_uk_socdist$date %>% summary()

df_uk_socdist <- df_uk_socdist %>% select(-runday, -frequ) %>%
  dplyr::rename(pers_o = open, 
                pers_c = sci,
                pers_e = extra,
                pers_a = agree,
                pers_n = neuro) %>% 
  select(-nuts3_name) %>% 
  dplyr::rename(socdist_tiles = all_day_bing_tiles_visited_relat,
                socdist_single_tile = all_day_ratio_single_tile_users) %>%
  drop_na()

df_uk_socdist
```

### Controls 
```{r}
df_uk_ctrl_nuts <- read_csv("controls_UK_nuts3.csv")
df_uk_ctrl_nuts <- df_uk_ctrl_nuts %>% select(-nuts3_name)
df_uk_ctrl_nuts


df_uk_ctrl_ut <- read_csv("controls_UK_ut.csv")
df_uk_ctrl_ut <- df_uk_ctrl_ut %>% select(-ut_name)
df_uk_ctrl_ut


```





### Merge prevalence data 
```{r}
df_uk_prev <- df_uk_prev %>% 
  plyr::join(df_uk_pers, by='ut_area') %>% 
  plyr::join(df_uk_ctrl_ut, by='ut_area')

# create sequence of dates
date_sequence <- seq.Date(min(df_uk_prev$date),
                          max(df_uk_prev$date), 1)
                     
# create data frame with time sequence
df_dates = tibble(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# merge day index with gps data
df_uk_prev = df_uk_prev %>% 
  merge(df_dates, by='date') %>% 
  arrange(ut_area) %>%
  as_tibble()

df_uk_prev
```

### Merge social distancing data
```{r}

nuts_ut_key <- read_csv('nuts3_ut.csv')
df_uk_socdist <- df_uk_socdist %>% plyr::join(df_uk_ctrl_nuts, by='nuts3')

df_uk_socdist <- nuts_ut_key %>% 
  inner_join(df_uk_socdist, by = c('nuts3')) %>%
  inner_join(select(df_uk_prev, ut_area, date, rate_day), by = c('ut_area', 'date')) %>%
  select(-ut_area)

# create sequence of dates
date_sequence <- seq.Date(min(df_uk_socdist$date),
                          max(df_uk_socdist$date), 1)
                     
# create data frame with time sequence
df_dates = tibble(date_sequence, 1:length(date_sequence)) 
names(df_dates) <- c('date', 'time')

# merge day index with gps data
df_uk_socdist = df_uk_socdist %>% 
  merge(df_dates, by='date') %>% 
  arrange(nuts3) %>%
  as_tibble()


df_uk_socdist

```

### Identify London areas
```{r}

nuts_london_inner <- c('UKI31','UKI32','UKI33','UKI34','UKI41',
                      'UKI42','UKI43','UKI44','UKI45')

nuts_london_outer <- c('UKI51','UKI52','UKI53','UKI54','UKI61',
                      'UKI62','UKI63','UKI71','UKI72','UKI73',
                      'UKI74','UKI75')

ut_london_inner <- c('E09000007','E09000001','E09000033','E09000013',
                    'E09000020','E09000032','E09000025','E09000012',
                    'E09000030','E09000014','E09000019','E09000023',
                    'E09000028','E09000022')

ut_london_outer <- c('E09000011','E09000004','E09000016','E09000002',
                    'E09000031','E09000026','E09000010','E09000006',
                    'E09000008','E09000029','E09000021','E09000024',
                    'E09000003','E09000005','E09000009','E09000017',
                    'E09000015','E09000018','E09000027')
```

```{r}

df_uk_prev = df_uk_prev %>% 
  mutate(london = ifelse(ut_area %in% ut_london_inner, 'london_inner', 
                       ifelse(ut_area %in% ut_london_outer, 'london_outer',
                              'country'))) %>%
  mutate(london = as.factor(london))

df_uk_socdist = df_uk_socdist %>% 
  mutate(london = ifelse(nuts3 %in% nuts_london_inner, 'london_inner', 
                       ifelse(nuts3 %in% nuts_london_outer, 'london_outer',
                              'country'))) %>%
  mutate(london = as.factor(london))

```

### Check timeframes 
```{r}
df_uk_prev$date %>% summary()
df_uk_socdist$date %>% summary()
```

### Control for weekend effect in social distancing
```{r}

df_uk_loess <- df_uk_socdist %>% 
  mutate(weekday = format(date, '%u')) %>% 
  filter(!weekday %in% c('6','7')) %>% 
  split(.$nuts3) %>%
  map(~ loess(socdist_single_tile ~ time, data = .)) %>%
  map(predict, 1:max(df_uk_socdist$time)) %>% 
  bind_rows() %>% 
  gather(key = 'nuts3', value = 'loess') %>% 
  group_by(nuts3) %>% 
  mutate(time = row_number())

df_uk_loess

df_uk_socdist <- df_uk_socdist %>% merge(df_uk_loess, by=c('nuts3', 'time')) %>% 
  mutate(weekday = format(date, '%u')) %>% 
  mutate(socdist_single_tile_clean = ifelse(weekday %in% c('6','7'), loess,
                                            socdist_single_tile)) %>%
  arrange(nuts3, time) %>% 
  select(-weekday)


df_uk_socdist <- df_uk_socdist %>% drop_na() %>% mutate(time = time-1)

```

# Explore data

### Plot prevalence over time
```{r}

df_uk_prev %>% ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=ut_area, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall prevalence over time")

pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

gg <- df_uk_prev %>% mutate(prev_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.2), quantile(.[[i]], 0.8), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(prev_tail != 'center') %>%
  ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=ut_area, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~prev_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```

### Explore differences between london and the rest 
```{r}

df_uk_prev %>% ggplot(aes(x=time, y=rate_day)) + 
  geom_point(aes(col=ut_area, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  facet_wrap(~london) +
  ggtitle("Overall prevalence over time")



```

### Plot social distancing over time
```{r}

df_uk_socdist %>% ggplot(aes(x=time, y=socdist_single_tile_clean)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  ggtitle("Overall social distancing over time")

pers <- c('pers_o', 'pers_c', 'pers_e', 'pers_a', 'pers_n')

for (i in pers){

gg <- df_uk_socdist %>% mutate(socdist_tail = cut(.[[i]], 
                                       breaks = c(-Inf, quantile(.[[i]], 0.2), quantile(.[[i]], 0.8), Inf),
                                       labels = c('lower tail', 'center', 'upper tail'))) %>% 
  filter(socdist_tail != 'center') %>%
  ggplot(aes(x=time, y=socdist_single_tile_clean)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  facet_wrap(~socdist_tail) + 
  theme(legend.position="none") +
  ggtitle(i)

print(gg)
}

```


```{r}
df_uk_socdist %>% ggplot(aes(x=time, y=socdist_single_tile_clean)) + 
  geom_point(aes(col=nuts3, size=popdens)) + 
  geom_smooth(method="loess", se=T) + 
  theme(legend.position="none") +
  facet_wrap(~london) +
  ggtitle("Overall social distancing over time")
```

```{r}

df_uk_socdist <- df_uk_socdist %>% mutate(socdist_single_tile = socdist_single_tile_clean) %>% 
  select(-loess, -socdist_single_tile_clean)

```

### Correlations
```{r}

df_uk_prev %>% group_by(ut_area) %>% 
  summarize_if(is.numeric, mean, na.rm=T) %>% 
  select(-ut_area, -time) %>% 
  cor(use = 'pairwise.complete') %>% round(3) %>%
  as.data.frame()

df_uk_socdist %>% group_by(nuts3) %>% 
  summarize_if(is.numeric, mean, na.rm=T) %>% 
  select(-nuts3, -time) %>% 
  cor(use = 'pairwise.complete') %>% round(3) %>% 
  as.data.frame()

```


## Rescale Data
```{r}
lvl2_scaled_ut <- df_uk_prev %>% 
  dplyr::select(-time, -date, -rate_day, -london) %>% 
  distinct() %>% 
  mutate_at(vars(-ut_area), scale)

lvl1_scaled_ut <- df_uk_prev %>% select(ut_area, time, rate_day)

df_uk_prev_scaled <- plyr::join(lvl1_scaled_ut, lvl2_scaled_ut, by = 'ut_area')

df_uk_prev_scaled
```


```{r}

lvl2_scaled_nuts <- df_uk_socdist %>% 
  dplyr::select(-time, -date, -london, 
                -socdist_tiles, -socdist_single_tile, -rate_day) %>% 
  distinct() %>% 
  mutate_at(vars(-nuts3), scale)

lvl1_scaled_nuts <- df_uk_socdist %>% select(nuts3, time, socdist_single_tile, rate_day) %>% 
  mutate_at(vars(-nuts3, -time, - rate_day), scale)

df_uk_socdist_scaled <- plyr::join(lvl1_scaled_nuts, lvl2_scaled_nuts, by = 'nuts3')

df_uk_socdist_scaled

```




# Predict Prevalence
### Extract first day of covid outbreak
```{r}

# get onset day
df_uk_onset_prev <- df_uk_prev_scaled %>% 
  group_by(ut_area) %>% 
  mutate(rate_cs = cumsum(rate_day)) %>% 
  filter(rate_cs > 0) %>%
  summarize(onset_prev = min(time))
  
# merge with county data
df_uk_onset_prev <- df_uk_prev_scaled %>% 
  select(-time, -rate_day) %>%
  distinct() %>% 
  left_join(df_uk_onset_prev, by = 'ut_area')

# handle censored data
df_uk_onset_prev <- df_uk_onset_prev %>% 
  mutate(event = ifelse(is.na(onset_prev), 0, 1)) %>% 
  mutate(onset_prev = replace_na(onset_prev, as.numeric(diff(range(df_uk_prev$date)))+1))

df_uk_onset_prev

```

### Extract slopes
```{r}

# cut time series before onset
df_uk_prev_scaled <- df_uk_prev_scaled %>% 
  group_by(ut_area) %>% 
  mutate(rate_cs = cumsum(rate_day)) %>% 
  filter(rate_cs > 0) %>%
  mutate(time = time-min(time)+1) %>%
  ungroup() %>%
  filter(time <= 30) %>%
  select(-rate_cs)

# drop counties with little data
df_uk_prev_scaled <- df_uk_prev_scaled %>%
  group_by(ut_area) %>%
  filter(n() == 30) %>%
  ungroup()

# extract slope prevalence
df_uk_slope_prev <- df_uk_prev_scaled %>% split(.$ut_area) %>% 
  map(~ lm(rate_day ~ time, data = .)) %>%
  map(coef) %>% 
  map_dbl('time') %>% 
  as.data.frame() %>% 
  rownames_to_column('ut_area') %>% 
  rename(slope_prev = '.')

# merge with county data
df_uk_slope_prev <- df_uk_prev_scaled %>% 
  select(-time, -rate_day) %>%
  distinct() %>% 
  inner_join(df_uk_slope_prev, by = 'ut_area') %>%
  drop_na()

```


### Explore distributions
```{r}

df_uk_onset_prev %>% ggplot(aes(onset_prev)) + geom_histogram()
df_uk_slope_prev %>% ggplot(aes(slope_prev)) + geom_histogram()

```


## Predict COVID onset with time-to-event regression 
```{r}

# predict onset from personality
cox_onset_prev <- coxph(Surv(onset_prev, event) ~ 
                          pers_o + pers_c + pers_e + pers_a + pers_n, 
                        data = df_uk_onset_prev)
cox_onset_prev %>% summary()

# predict onset from personality with controls
cox_onset_prev_ctrl <- coxph(Surv(onset_prev, event) ~ 
                               pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative,
                             data = df_uk_onset_prev)
cox_onset_prev_ctrl %>% summary()

```

## Predict prevalence slopes with linear models
```{r}

# predict slopes from personality
lm_slope_prev <- lm(slope_prev ~ pers_o + pers_c + pers_e + pers_a + pers_n, 
                         data = df_uk_slope_prev)
lm_slope_prev %>% summary()

# predict slopes from personality with controls
lm_slope_prev_ctrl <- lm(slope_prev ~  
                               pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative,
                         data = df_uk_slope_prev)
lm_slope_prev_ctrl %>% summary()

```

### CRF predicting slopes
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_slope_prev <- cforest(slope_prev ~  
                               pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative,
                           data = df_uk_slope_prev, 
                         controls = ctrls)

crf_slope_prev_varimp <- varimp(crf_slope_prev, nperm = 1)
crf_slope_prev_varimp_cond <- varimp(crf_slope_prev, conditional = T, nperm = 1)

crf_slope_prev_varimp %>% as.data.frame() %>% 
  rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(angle = 90))

crf_slope_prev_varimp_cond %>% as.data.frame() %>% 
  rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90))

```

## Predict Social Distancing
### Change point analysis
```{r}

# keep only counties with full data
nuts_complete <- df_uk_socdist_scaled %>% 
  group_by(nuts3) %>% 
  summarize(n = n()) %>% 
  filter(n==max(.$n)) %>% 
  .$nuts3

# run changepoint analysis
df_uk_socdist_cpt_results <- df_uk_socdist_scaled %>% 
  select(nuts3, socdist_single_tile) %>%
  filter(nuts3 %in% nuts_complete) %>% 
  split(.$nuts3) %>%
  map(~ cpt.meanvar(as.vector(.$socdist_single_tile),
                    #penalty = 'Asymptotic',
                    class=TRUE,
                    param.estimates=TRUE,
                    Q=1,
                    test.stat = 'Normal'))

# calculate change point
df_uk_socdist_cpt_day <- df_uk_socdist_cpt_results %>% 
  map(cpts) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(cpt_day_socdist = '.') %>%
  rownames_to_column('nuts3')

# calculate mean differences
df_uk_socdist_cpt_mean_diff <- df_uk_socdist_cpt_results %>% 
  map(param.est) %>% 
  map(~ .$mean) %>% 
  map(~ .[2]-.[1]) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(mean_diff_socdist = '.') %>%
  rownames_to_column('nuts3')

# calculate varaince differences
df_uk_socdist_cpt_var_diff <- df_uk_socdist_cpt_results %>% 
  map(param.est) %>% 
  map(~ .$variance) %>% 
  map(~ .[2]-.[1]) %>% 
  unlist() %>% 
  as.data.frame() %>% 
  rename(var_diff_socdist = '.') %>%
  rownames_to_column('nuts3')

# merge with county data
df_uk_cpt_socdist <- df_uk_socdist_scaled %>% 
  select(-time, -rate_day, -socdist_single_tile) %>%
  distinct() %>% 
  left_join(df_uk_socdist_cpt_day, by='nuts3') %>%
  left_join(df_uk_socdist_cpt_mean_diff, by='nuts3') %>%
  left_join(df_uk_socdist_cpt_var_diff, by='nuts3') %>%
  left_join(nuts_ut_key, by='nuts3') %>% 
  left_join(select(df_uk_onset_prev, ut_area, onset_prev), by='ut_area') %>%
  left_join(select(df_uk_slope_prev, ut_area, slope_prev), by='ut_area') %>%
  select(-ut_area)

# handle censored data
df_uk_cpt_socdist <- df_uk_cpt_socdist %>% 
  mutate(cpt_day_socdist = ifelse(is.na(cpt_day_socdist), 
                                  as.numeric(diff(range(df_us$date))), 
                                  cpt_day_socdist)) %>% 
  mutate(event = ifelse(cpt_day_socdist >= 60, 0, 1))

```

```{r}
df_uk_cpt_socdist$cpt_day_socdist %>% hist()
df_uk_cpt_socdist$mean_diff_socdist %>% hist()
df_uk_cpt_socdist$var_diff_socdist %>% hist()

```

```{r}

for(i in head(df_uk_socdist_cpt_results, 5)){
  plot(i)
}

```


# Predicting change points with time-to-event regression 
```{r}

# predict hazard from personality
cox_cpt_socdist <- coxph(Surv(cpt_day_socdist, event) ~ 
                           pers_o + pers_c + pers_e + pers_a + pers_n, 
                  data = df_uk_cpt_socdist)
cox_cpt_socdist %>% summary()

# predict hazard from personality with controls
cox_cpt_socdist_ctrl <- coxph(Surv(cpt_day_socdist, event) ~ 
                                pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative,
                  data = df_uk_cpt_socdist)
cox_cpt_socdist_ctrl %>% summary()

# predict hazard from personality with controls
cox_cpt_socdist_ctrl2 <- coxph(Surv(cpt_day_socdist, event) ~ 
                                 pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative + onset_prev + slope_prev,
                  data = df_uk_cpt_socdist)
cox_cpt_socdist_ctrl2 %>% summary()

```

### Linear models predicting mean differences
```{r}

lm_meandiff_socdist <- lm(mean_diff_socdist ~ 
                            pers_o + pers_c + pers_e + pers_a + pers_n, 
                         data = df_uk_cpt_socdist)
lm_meandiff_socdist %>% summary()

lm_meandiff_socdist_ctrl <- lm(mean_diff_socdist ~ 
                                 pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative,
                            data = df_uk_cpt_socdist)
lm_meandiff_socdist_ctrl %>% summary()

lm_meandiff_socdist_ctrl2 <- lm(mean_diff_socdist ~ 
                                  pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative + onset_prev + slope_prev,
                            data = df_uk_cpt_socdist)
lm_meandiff_socdist_ctrl2 %>% summary()

```

### CRF predicting mean difference
```{r}

ctrls <- cforest_unbiased(ntree=500, mtry=5)

crf_meandiff_socdist <- cforest(mean_diff_socdist ~ 
                                  pers_o + pers_c + pers_e + pers_a + pers_n +
                               airport_dist + males + popdens + manufacturing + 
                               tourism + health + academic + medinc + medage +
                               conservative + onset_prev + slope_prev,
                               data = df_uk_cpt_socdist %>% drop_na(),
                         controls = ctrls)

crf_meandiff_socdist_varimp <- varimp(crf_meandiff_socdist, nperm = 1)
crf_meandiff_socdist_varimp_cond <- varimp(crf_meandiff_socdist, conditional = T, nperm = 1)

crf_meandiff_socdist_varimp %>% as.data.frame() %>% 
  rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90))

crf_meandiff_socdist_varimp_cond %>% as.data.frame() %>% 
  rownames_to_column('variable') %>%
  ggplot(aes(x=variable, y=.)) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90))

```